---
title: "FESOM_REcoM_LR Random subset variable A"
author: "Jens Daniel Müller"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  workflowr::wflow_html:
    number_sections: true
    toc_depth: 3
    toc_float:
      collapsed: false
editor_options:
  chunk_output_type: console
---

```{r parent, child = "/nfs/kryo/work/jenmueller/emlr_cant/utilities/setup.Rmd"}
# this chunk runs the code stored in setup.Rmd
# if required, please refer to instructions given here:
# https://jdblischak.github.io/workflowr/articles/wflow-07-common-code.html
```

```{r define_paths}
path_GLODAP_preprocessing <-
  paste(path_root, "/observations/preprocessing/", sep = "")

path_cmorized <-
  "/nfs/kryo/work/updata/reccap2/Models/3D_ALL/FESOM_REcoM_LR_3D_all_v20210712/"

path_preprocessing <-
  paste(path_root, "/model/preprocessing/FESOM_REcoM_LR/", sep = "")
```

```{r load_libraries_specific, include=FALSE}
library(stars)
library(lubridate)
library(rqdatatable)
library(gsw)
library(marelac)
library(tidync)
```

```{r select_basin_mask}

# use only three basin to assign general basin mask
# ie this is not specific to the MLR fitting
basinmask <- basinmask %>%
  filter(MLR_basins == "2") %>%
  select(lat, lon, basin_AIP)

```

# Read GLODAPv2_2021 preprocessed files

```{r read_GLODAPv2_2021_preprocessed_file}

GLODAP <-
  read_csv(paste(path_GLODAP_preprocessing,
                 "GLODAPv2.2021_preprocessed.csv",
                 sep = ""))

GLODAP <- GLODAP %>%
  mutate(month = month(date))

```

# Randomly subset model data

Here we randomly subset cmorized (1x1) model with variable forcing, according to the total number of GLODAP observations for the whole period from a previously cleaned file. The number for the annual subset remains the same for each year, which could be expressed by the total number of observations divided by number of years.

Besides, Model results are given in [mol m^-3^], whereas GLODAP data are in [µmol kg^-1^]. This refers to the variables:

- DIC  
- ALK  
- O2  
- NO3  
- PO4  
- SiO3  
- AOU (calculated)

For comparison, model results were converted from [mol m^-3^] to [µmol kg^-1^]

```{r random_subset_cmorized_variable_forcing_data, eval=FALSE}

# read in a random model
model <-
  tidync(
    paste(
      path_cmorized,
      "dissic_FESOM_REcoM_LR_A_1_gr_1980-2018_v20210712.nc",
      sep = ""
    )
  ) %>%
  hyper_tibble() %>%
  drop_na()

# convert longitudes and mutate month
model <- model %>%
  rename(
    time = Time,
    lon = Lon,
    lat = Lat,
    depth = Depth
  ) %>%
filter(time == min(time)) %>%
  mutate(lon = if_else(lon < 20, lon + 360, lon))

# only consider model grids within basinmask
model <- inner_join(model, basinmask)

# model grid with depth
model_grid_depth <- model %>%
  select(lon, lat, depth)

rm(model)

# for loop across years
years <- c("1982":"2018")

# set equal number of random model sampling will be made for each year
n = floor(nrow(GLODAP) / length(years))

for (i_year in years) {
  # i_year <- years[1]
  
  # random sample n = GLODAP / years from model grid depth
  model_resample_grid_depth_temp <-
    sample_n(model_grid_depth, n) %>%
    arrange(lon, lat, depth) %>%
    mutate(year = i_year)
  
  # add random sample model grid depth for each year together
  if (exists("model_resample_grid_depth")) {
    model_resample_grid_depth <-
      bind_rows(model_resample_grid_depth, model_resample_grid_depth_temp)
  }
  
  if (!exists("model_resample_grid_depth")) {
    model_resample_grid_depth <- model_resample_grid_depth_temp
  }
  
}

# set name of model to be subsetted
model_ID <- "A"

# for loop across variables
variables <-
  c("so", "thetao", "dissic", "talk", "o2", "no3", #"po4", 
    "si")

for (i_variable in variables) {
  # i_variable <- variables[1]
  
  # read list of all files
  file <-
    list.files(
      path = path_cmorized,
      pattern = paste(
        "^",
        i_variable,
        "_FESOM_REcoM_LR_",
        model_ID,
        "_1_gr_1980-2018_v20210712.nc",
        sep = ""
      )
    )
  print(file)
  
  # read in data
  variable_data <-
    tidync(paste(path_cmorized,
                 file,
                 sep = ""),
           make_units = FALSE)
  
  # convert to tibble
  variable_data_tibble <- variable_data %>%
    hyper_tibble()
  
  # remove open link to nc file
  rm(variable_data)
  
  # remove na values
  variable_data_tibble <-
    variable_data_tibble %>%
    filter(!is.na(!!sym(i_variable)))
  
  # convert variable name
  variable_data_tibble <- variable_data_tibble %>%
    rename(
      year = Time,
      lon = Lon,
      lat = Lat,
      depth = Depth
    )
  
  # convert longitudes
  variable_data_tibble <- variable_data_tibble %>%
    mutate(lon = if_else(lon < 20, lon + 360, lon))
  
  # only consider model grids within basinmask
  variable_data_tibble <-
    inner_join(variable_data_tibble, basinmask) %>%
    select(-basin_AIP)
  
  # add random sample model subset for each variable together
  if (exists("model_resample")) {
    model_resample <-
      left_join(model_resample, variable_data_tibble)
  }
  
  if (!exists("model_resample")) {
    model_resample <-
      left_join(model_resample_grid_depth, variable_data_tibble)
  }
  
}

# calculate model temperature
model_resample <- model_resample %>%
  mutate(temp = gsw_pt_from_t(
    SA = so,
    t = thetao,
    p = 10.1325,
    p_ref = depth
  ))

# unit transfer from mol/m3 to µmol/kg
model_resample <- model_resample %>%
  mutate(
    rho = gsw_pot_rho_t_exact(
      SA = so,
      t = temp,
      p = depth,
      p_ref = 10.1325
    ),
    dissic = dissic * (1e+6 / rho),
    talk = talk * (1e+6 / rho),
    o2 = o2 * (1e+6 / rho),
    no3 = no3 * (1e+6 / rho),
#    po4 = po4 * (1e+6 / rho),
    si = si * (1e+6 / rho)
  )

# calculate AOU
model_resample <- model_resample %>%
  mutate(
    oxygen_sat_m3 = gas_satconc(
      S = so,
      t = temp,
      P = 1.013253,
      species = "O2"
    ),
    oxygen_sat_kg = oxygen_sat_m3 * (1e+3 / rho),
    aou = oxygen_sat_kg - o2
  ) %>%
  select(-oxygen_sat_kg,-oxygen_sat_m3)

# rename as variable
model_resample <- model_resample %>%
  rename(
    sal = so,
    theta = thetao,
    temp = temp,
    tco2 = dissic,
    talk = talk,
    oxygen = o2,
    nitrate = no3,
#    phosphate = po4,
    silicate = si,
    aou = aou
  )

# calculate gamma
library(oce)
library(gsw)

model_resample <- model_resample %>% 
  mutate(CTDPRS = gsw_p_from_z(-depth,
                               lat))

model_resample <- model_resample %>% 
  mutate(THETA = swTheta(salinity = sal,
                         temperature = temp,
                         pressure = CTDPRS,
                         referencePressure = 0,
                         longitude = lon-180,
                         latitude = lat))

model_resample <- model_resample %>% 
  rename(LATITUDE = lat,
         LONGITUDE = lon,
         SALNTY = sal)

library(reticulate)
source_python(
  paste(
    path_root,
    "/utilities/functions/python_scripts/",
    "Gamma_GLODAP_python.py",
    sep = ""
  )
)

model_resample <- calculate_gamma(model_resample)

model_resample <- model_resample %>%
  rename(lat = LATITUDE,
         lon = LONGITUDE,
         sal = SALNTY,
         gamma = GAMMA) %>%
  select(-CTDPRS, -THETA)

# add basin mask
model_resample <- inner_join(model_resample, basinmask)

# write file for random model sampling
model_resample %>%
  write_csv(paste(path_preprocessing,
                  "GLODAPv2.2021_preprocessed_model_runA_random_subset_grid_ann.csv",
                  sep = ""))

```

# Control plots

## Spatial distribution

```{r random_sample_distribution_maps}

# read in random model sampling file
model_resample <-
  read_csv(paste(path_preprocessing,
                 "GLODAPv2.2021_preprocessed_model_runA_random_subset_grid_ann.csv",
                 sep = ""))

# plot random sampling cmorized grids in each year
years <- c("1982", "1990", "2000", "2010", "2018")
for (i_year in years) {
  # i_year <- years[1]
  
  model_resample_year <- model_resample %>%
    filter(year == i_year)
  
  print(
    map +
      geom_bin2d(data = model_resample_year,
                 aes(lon, lat),
                 binwidth = 1) +
      scale_fill_viridis_c(direction = -1) +
      coord_quickmap(expand = 0) +
      labs(
        title = paste("Random Model Sampling of year", i_year),
        subtitle = paste("Nr of observations", nrow(model_resample_year)),
        x = "Longitude",
        y = "Latitude"
      )
  )

}

```

## Depth distribution

```{r random_sample_depth_distribution}

# Calculate and plot depth distribution of model subset
model_resample_depth <- model_resample %>%
  count(depth, year)

model_resample_depth_average <- model_resample_depth %>%
  group_by(depth) %>%
  summarise(n = mean(n))

model_resample_depth_average %>%
  arrange(depth) %>%
  ggplot(aes(n, depth)) +
  geom_point(data = model_resample_depth,
             aes(n, depth, col = "All years")) +
  geom_point(aes(n, depth, col = "Average")) +
  geom_path(aes(n, depth, col = "Average")) +
  scale_color_brewer(palette = "Set1",
                     name = "",
                     direction = -1) +
  scale_y_reverse() +
  coord_cartesian(xlim = c(0,500),
                  ylim = c(6000,0)) +
  labs(title = "Depth distribution of random model subset")

```

```{r GLODAP_depth_distribution}

# Calculate and plot depth distribution of GLODAP data
# Depths gridded to model depth levels for comparison
GLODAP_depth <- GLODAP %>%
  mutate(depth = as.numeric(as.character(cut(depth,
                     unique(model_resample_depth_average$depth),
                     labels = unique(model_resample_depth_average$depth)[2:46])))) %>% 
  count(depth, year)

GLODAP_depth_average <- GLODAP_depth %>%
  group_by(depth) %>%
  summarise(n = mean(n))

GLODAP_depth_average %>%
  arrange(depth) %>%
  ggplot(aes(n, depth)) +
  geom_point(data = GLODAP_depth,
             aes(n, depth, col = "All years")) +
  geom_point(aes(n, depth, col = "Average")) +
  geom_path(aes(n, depth, col = "Average")) +
  scale_color_brewer(palette = "Set1",
                     name = "",
                     direction = -1) +
  scale_y_reverse() +
  coord_cartesian(xlim = c(0,500),
                  ylim = c(6000,0)) +
  labs(title = "Depth distribution of GLODAP observations")

```

```{r resample_with_less_high_lat_points, eval=FALSE}

# read in random model sampling file
resample_grid <-
  read_csv(paste(path_preprocessing,
                 "GLODAPv2.2021_preprocessed_model_runA_random_subset_grid_ann.csv",
                 sep = ""))

for (i in unique(resample_grid$lat)) {
  # i <- unique(model_resample$lat)[1]
  
  resample_grid_lat <- resample_grid %>%
    filter(lat == i)
  
  n <- nrow(resample_grid_lat)
  
  resample_grid_lat <- sample_n(resample_grid_lat, floor(n*cospi(i/180)))
  
  # resample the random subset according to the latitude
  if (exists("resample_lat")) {
    resample_lat <-
      bind_rows(resample_lat, resample_grid_lat)
  }
  
  if (!exists("resample_lat")) {
    resample_lat <- resample_grid_lat
  }
  
}

# write resampling file
resample_lat %>%
  write_csv(paste(path_preprocessing,
                 "GLODAPv2.2021_preprocessed_model_runA_random_subset_lat_ann.csv",
                 sep = ""))

```

# Spatial distribution

```{r random_resample_distribution_maps}

# read in random model sampling file
resample_lat <-
  read_csv(paste(path_preprocessing,
                 "GLODAPv2.2021_preprocessed_model_runA_random_subset_lat_ann.csv",
                 sep = ""))

# plot random sampling cmorized grids in each year
years <- c("1982", "1990", "2000", "2010", "2018")
for (i_year in years) {
  # i_year <- years[1]
  
  resample_lat_year <- resample_lat %>%
    filter(year == i_year)
  
  print(
    map +
      geom_bin2d(data = resample_lat_year,
                 aes(lon, lat),
                 binwidth = 1) +
      scale_fill_viridis_c(direction = -1) +
      coord_quickmap(expand = 0) +
      labs(
        title = paste("Random model resampling with lat of year", i_year),
        subtitle = paste("Nr of observations", nrow(resample_lat_year)),
        x = "Longitude",
        y = "Latitude"
      )
  )

}

```
