---
title: "Climatology variable A"
author: "Jens Daniel Müller"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  workflowr::wflow_html:
    number_sections: true
    toc_depth: 3
    toc_float:
      collapsed: false
editor_options:
  chunk_output_type: console
---

```{r parent, child = "/nfs/kryo/work/jenmueller/emlr_cant/utilities/setup.Rmd"}
# this chunk runs the code stored in setup.Rmd
# if required, please refer to instructions given here:
# https://jdblischak.github.io/workflowr/articles/wflow-07-common-code.html
```

```{r define_paths, include=FALSE}
path_cmorized <-
  "/nfs/kryo/work/updata/reccap2/Models/3D_ALL/"

path_preprocessing <-
  paste0(path_root, "/model/preprocessing/Climatology_A_2007_all_models/")

```

```{r library, include=FALSE}
library(stars)
library(lubridate)
library(reticulate)
library(oce)
library(gsw)
library(geosphere)
library(marelac)
```

# Select basin mask

```{r select_basin_mask}

# use only three basin to assign general basin mask
# ie this is not specific to the MLR fitting
basinmask <- basinmask %>%
  filter(MLR_basins == "2") %>%
  select(lat, lon, basin_AIP)

```


# Read nc file

Here we used annual output of cmorized (1x1) model with variable forcing (RECCAP2 RunA) in year 2007 as the predictor climatology. Predictors include:

- Salinity (sal)
- Potential temperature (theta, not predictor, used for temperature calculation)
- In-situ temperature (temp, calculated)
- DIC (tco2)
- ALK (talk)
- oxygen
- AOU (calculated)
- nitrate
- phosphate
- silicate


```{r create_list_of_models}

# set name of model to be subsetted
model_ID <- "A"

# for loop across variables
variables <-
  c("so", "thetao", "dissic", "talk", "o2", "no3", "po4", "si")


models <- list.files(path_cmorized)

models <-
  models[!str_detect(models, pattern = "\\.t|\\.z")]

models <-
  models[str_detect(
    models,
    pattern = c(
      "CESM|CNRM|EC-Earth3|FESOM_REcoM_LR|MOM6-Princeton|MRI-ESM2-0|NorESM-OC1.2|ORCA025-GEOMAR|ORCA1-LIM3-PISCES"
    )
  )]


# files chunked into decades
models <-
  models[!str_detect(models, pattern = "ORCA025-GEOMAR")]

# "so" variable only NA's
models <-
  models[!str_detect(models, pattern = "MOM6-Princeton")]

```

```{r load_gamma_calculation_scripts}

# load python scripts
source_python(paste0(
  path_functions,
  "python_scripts/Gamma_GLODAP_python.py"
))

```



```{r read_climatology_fields_2007}

# models <- models[1]

for (i_model in models) {
  # i_model <- models[8]
  print(i_model)
  
  variables_available <-
    list.files(path = paste0(path_cmorized, i_model),
               pattern = paste0("_", model_ID, "_"))
  
  variables_available <-
    str_split(variables_available,
              pattern = "_",
              simplify = TRUE)[, 1]
  variables_available <-
    variables_available[variables_available %in% variables]
  variables_available <- unique(variables_available)
  print(variables_available)
  
  for (i_variable in variables_available) {
    # i_variable <- variables_available[1]
    
    # read list of all files
    file <-
      list.files(path = paste0(path_cmorized, i_model),
                 pattern = paste0(i_variable, "_"))
    
    file <-
      file[str_detect(file, pattern = paste0("_", model_ID, "_"))]
    
    print(file)
    
    # read in data
    if (i_model == "NorESM-OC1.2_3D_ALL_v20211125") {
      variable_data <-
        tidync::tidync(paste(paste0(path_cmorized, i_model),
                             file,
                             sep = "/"))
    } else {
      variable_data <-
        read_ncdf(paste(paste0(path_cmorized, i_model),
                        file,
                        sep = "/"),
                  make_units = FALSE)
    }
    
    if (i_model == "CESM-ETHZ_3D_ALL_v20211122") {
      variable_data <-
        variable_data %>% slice(index = 28, along = "time_ann")
    } else if (i_model == "FESOM_REcoM_LR_3D_all_v20211119") {
      variable_data <-
        variable_data %>% slice(index = 28, along = "Time")
    } else if (i_model == "planktom12_3d_all_v20220404") {
      variable_data <-
        variable_data %>% slice(index = 28, along = "TIME")
    } else if (i_model == "MRI-ESM2-0_3D_ALL_v20210830" &
               i_variable == "si") {
      variable_data <-
        variable_data %>% slice(index = 1, along = "time")
    } else if (i_model == "NorESM-OC1.2_3D_ALL_v20211125") {
      variable_data <- variable_data %>%
        tidync::hyper_filter(time = index == 28) %>%
        tidync::hyper_tibble() %>%
        select(-time)
    } else {
      variable_data <- variable_data %>% slice(index = 28, along = "time")
    }
    
    print(variable_data)
    
    # convert to tibble
    variable_data_tibble <- variable_data %>%
      as_tibble()
    
    # remove open link to nc file
    rm(variable_data)
    
    # remove na values
    variable_data_tibble <-
      variable_data_tibble %>%
      filter(!is.na(!!sym(i_variable)))
    

    if (i_model == "CNRM-ESM2-1_3D_ALL_v20211208") {
      variable_data_tibble <- variable_data_tibble %>%
        rename(depth = lev)
    }
    
    if (i_model == "FESOM_REcoM_LR_3D_all_v20211119") {
      variable_data_tibble <- variable_data_tibble %>%
        rename(
          lat = Lat,
          lon = Lon,
          depth = Depth
        )
      }
    
    if (i_model == "MOM6-Princeton_3D_ALL_v20220125") {
      variable_data_tibble <- variable_data_tibble %>%
        rename(depth = z_l)
    }
    
    if (i_model == "MRI-ESM2-0_3D_ALL_v20210830") {
      variable_data_tibble <- variable_data_tibble %>%
        rename(depth = lev)
    }
    
    if (i_model == "planktom12_3d_all_v20220404") {
      variable_data_tibble <- variable_data_tibble %>%
        rename(lon = LONGITUDE,
               lat = LATITUDE,
               depth = DEPTH)
    }
    
    
    # harmonize longitudes
    variable_data_tibble <- variable_data_tibble %>%
      mutate(lon = if_else(lon < 20, lon + 360, lon))
    
    # only consider model grids within basinmask
    variable_data_tibble <-
      inner_join(variable_data_tibble, basinmask) %>%
      select(-basin_AIP)
    
    
    if (exists("climatology")) {
      climatology <- full_join(climatology, variable_data_tibble)
    }
    
    if (!exists("climatology")) {
      climatology <- variable_data_tibble
    }
    
    
  }
  
  if (i_model == "FESOM_REcoM_LR_3D_all_v20211119") {
    climatology <- climatology %>%
      mutate(po4 = NA)
  }

  if (i_model == "planktom12_3d_all_v20220404") {
    climatology <- climatology %>%
      mutate(no3 = NA)
  }
  
  climatology <- climatology %>%
    rename(
      sal = so,
      THETA = thetao,
      tco2 = dissic,
      talk = talk,
      oxygen = o2,
      nitrate = no3,
      phosphate = po4,
      silicate = si
    )
  
  climatology <- climatology %>%
    mutate(depth = round(depth))
  
  
  
  # In-situ temperature
  climatology <- climatology %>%
    mutate(temp = gsw_pt_from_t(
      SA = sal,
      t = THETA,
      p = 10.1325,
      p_ref = depth
    ))
  
  # Example profile from North Atlantic Ocean
  print(
  climatology %>%
    filter(lat == params_global$lat_Atl_profile,
           lon == params_global$lon_Atl_section) %>%
    ggplot() +
    geom_line(aes(temp, depth, col = "insitu")) +
    geom_point(aes(temp, depth, col = "insitu")) +
    geom_line(aes(THETA, depth, col = "theta")) +
    geom_point(aes(THETA, depth, col = "theta")) +
    scale_y_reverse() +
    labs(title = i_model) *
    scale_color_brewer(palette = "Dark2", name = "Scale"))
  
  # Unit conversion
  # Model results are given in [mol m^-3^], whereas GLODAP data are in [µmol kg^-1^].
  # For comparison, model results were converted from [mol m^-3^] to [µmol kg^-1^]
  climatology <- climatology %>%
    mutate(
      rho = gsw_pot_rho_t_exact(
        SA = sal,
        t = temp,
        p = depth,
        p_ref = 10.1325
      ),
      tco2 = tco2 * (1e+06 / rho),
      talk = talk * (1e+06 / rho),
      oxygen = oxygen * (1e+06 / rho),
      nitrate = nitrate * (1e+06 / rho),
      phosphate = phosphate * (1e+06 / rho),
      silicate = silicate * (1e+06 / rho)
    )
  
  
  
  # AOU calculation
  climatology <- climatology %>%
    mutate(
      oxygen_sat_m3 = gas_satconc(
        S = sal,
        t = temp,
        P = 1.013253,
        species = "O2"
      ),
      oxygen_sat_kg = oxygen_sat_m3 * (1e+3 / rho),
      AOU = oxygen_sat_kg - oxygen
    ) %>%
    select(-oxygen_sat_kg, -oxygen_sat_m3)
  
  
  
  # Neutral density calculation
  # Neutral density gamma was calculated with a Python script provided by Serazin et al (2011)
  # which performs a polynomial approximation of the original gamma calculation.
  
  #calculate pressure from depth
  climatology <- climatology %>%
    mutate(CTDPRS = gsw_p_from_z(-depth,
                                 lat))
  
  # rename variables according to python script
  climatology_gamma_prep <- climatology %>%
    rename(LATITUDE = lat,
           LONGITUDE = lon,
           SALNTY = sal)
  
  # calculate gamma
  climatology_gamma_calc <-
    calculate_gamma(climatology_gamma_prep)
  
  # reverse variable naming
  climatology <- climatology_gamma_calc %>%
    select(-c(CTDPRS, THETA)) %>%
    rename(
      lat = LATITUDE,
      lon = LONGITUDE,
      sal = SALNTY,
      gamma  = GAMMA
    )
  
  climatology <- as_tibble(climatology)
  
  rm(climatology_gamma_calc, climatology_gamma_prep)
  
  # write_climatology_predictor_file
  # select relevant columns
  climatology <- climatology %>%
    select(-c(rho))
  
  # Remove 3D_all from model name
  i_model <- str_remove(i_model, "3D_ALL_|3D_all_")
  
  # write csv file
  climatology %>%
    write_csv(paste0(path_preprocessing,
                     i_model,
                     "_climatology_runA_2007.csv"))
  
  rm(climatology)
  
}

```

# Plots

Below, following subsets of the climatology are plotted for all relevant predictors:  

- Horizontal planes at 4 depth levels
- Global section along track indicated by white lines in maps.

```{r read_climatologies}


climatology_files <- fs::dir_ls(path_preprocessing)

climatology <- climatology_files %>% 
  map_dfr(read_csv, .id = "model")

climatology <- climatology %>% 
  mutate(model = str_remove(model, path_preprocessing),
         model = str_remove(model, "_climatology_runA_2007.csv"))


```



```{r climatology_maps_and_sections, eval=FALSE}

# define plotting variables
vars <- c(
  "tco2",
  "talk",
  "sal",
  "nitrate",
  "phosphate",
  "silicate",
  "oxygen",
  "temp",
  "AOU",
  "gamma"
)

# i_var <- vars[1]

for (i_var in vars) {
  # i_var <- vars[1]
  
  
  # plot sections
  print(p_section_global(df = climatology %>%
                     filter(model == models[1]),
                   var = i_var))
  
}

```
