---
title: "FESOM_REcoM_LR Climatology variable A"
author: "Jens Daniel Müller"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  workflowr::wflow_html:
    number_sections: true
    toc_depth: 3
    toc_float:
      collapsed: false
editor_options:
  chunk_output_type: console
---

```{r parent, child = "/nfs/kryo/work/jenmueller/emlr_cant/utilities/setup.Rmd"}
# this chunk runs the code stored in setup.Rmd
# if required, please refer to instructions given here:
# https://jdblischak.github.io/workflowr/articles/wflow-07-common-code.html
```

```{r define_paths, include=FALSE}
path_cmorized       <- "/nfs/kryo/work/updata/reccap2/Models/3D_ALL/FESOM_REcoM_LR_3D_all_v20210218/"
path_preprocessing  <- paste(path_root, "/model/preprocessing/FESOM_REcoM_LR/", sep = "")
```

```{r library, include=FALSE}
library(tidync)
library(reticulate)
library(oce)
library(gsw)
library(geosphere)
library(marelac)
```


# Read nc file

Here we used annual output of cmorized (1x1) model with variable forcing (RECCAP2 RunA) in year 2007 as the predictor climatology. Predictors include:

- Salinity (sal)
- Potential temperature (theta, not predictor, used for temperature calculation)
- In-situ temperature (temp, calculated)
- DIC (tco2)
- ALK (talk)
- oxygen
- AOU (calculated)
- nitrate
- phosphate
- silicate


```{r read_and_calculate_climatology}

# set name of model to be subsetted
model_ID <- "A"

# for loop across variables
# 3d variables  -----  No po4 for this model !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
variables <-
  c("so", "thetao", "dissic", "talk", "o2", "no3",  #"po4", 
    "si")

for (i_variable in variables) {
  # i_variable <- variables[1]
  
  # read list of all files
  file <-
    list.files(
      path = path_cmorized,
      pattern = paste(
        "^",
        i_variable,
        "_FESOM_REcoM_LR_",
        model_ID,
        "_1_gr_1980-2018_v20210218.nc",
        sep = ""
      )
    )
  print(file)
  
  # read in data
  variable_data <-
    tidync(paste(path_cmorized,
                    file,
                    sep = ""),
              make_units = FALSE)
  
  # convert to tibble
  variable_data_tibble <- variable_data %>%
    hyper_tibble()
  
  # remove open link to nc file
  rm(variable_data)
  
  # remove na values
  variable_data_tibble <-
    variable_data_tibble %>%
    filter(!is.na(!!sym(i_variable)))
  
  # convert variable name
  variable_data_tibble <- variable_data_tibble %>%
    rename(year = Time,
           lon = Lon,
           lat = Lat,
           depth = Depth)
  
  # select data of 2007 as the climatology
  climatology_temp <- variable_data_tibble %>%
    filter(year == 2007)
  
  # # calculate climatology
  # climatology_temp <- variable_data_tibble %>%
  #   select(-time) %>%
  #   group_by(lon, lat, depth) %>%
  #   mutate(!!sym(i_variable) := mean(!!sym(i_variable))) %>%
  #   ungroup() %>%
  #   unique()
  
  if (exists("climatology")) {
    climatology <- left_join(climatology, climatology_temp)
  }
  
  if (!exists("climatology")) {
    climatology <- climatology_temp
  }
  
}

# harmonize longitudes
climatology <- climatology %>%
    rename(
    sal = so,
    THETA = thetao,
    tco2 = dissic,
    talk = talk,
    oxygen = o2,
    nitrate = no3,
 #   phosphate = po4,
    silicate = si
  ) %>%
  select(lon, lat, depth, sal, THETA, tco2, talk, oxygen, nitrate, #phosphate,
         silicate) %>%
  mutate(lon = if_else(lon < 20, lon + 360, lon))

rm(climatology_temp)

```

## Round depth levels

```{r round_depth_levels}

climatology <- climatology %>%
  mutate(depth = round(depth))

```


# Apply basin mask

```{r apply_basin_mask}

# use only three basin to assign general basin mask
# ie this is not specific to the MLR fitting
basinmask <- basinmask %>% 
  filter(MLR_basins == "2") %>% 
  select(lat, lon, basin_AIP)

# restrict predictor fields to basin mask grid
climatology <- inner_join(climatology, basinmask)

```


# In-situ temperature

In-situ temperature was calculated as input paramter for AOU calculation.

```{r calc_insitu_temp}

climatology <- climatology %>%
  mutate(temp = gsw_pt_from_t(
    SA = sal,
    t = THETA,
    p = 10.1325,
    p_ref = depth
  ))

```


Example profile from North Atlantic Ocean.

```{r temp_theta_profile_plot}

climatology %>%
  filter(lat == params_global$lat_Atl_profile,
         lon == params_global$lon_Atl_section) %>%
  ggplot() +
  geom_line(aes(temp, depth, col = "insitu"), orientation = "y") +
  geom_point(aes(temp, depth, col = "insitu")) +
  geom_line(aes(THETA, depth, col = "theta"), orientation = "y") +
  geom_point(aes(THETA, depth, col = "theta")) +
  scale_y_reverse() +
  scale_color_brewer(palette = "Dark2", name = "Scale")

```


# Unit conversion

Model results are given in [mol m^-3^], whereas GLODAP data are in [µmol kg^-1^].

For comparison, model results were converted from [mol m^-3^] to [µmol kg^-1^]

```{r unit_conversion}

# unit conversion from mol/m3 to µmol/kg
climatology <- climatology %>%
  mutate(
    rho = gsw_pot_rho_t_exact(
      SA = sal,
      t = temp,
      p = depth,
      p_ref = 10.1325
    ),
    tco2 = tco2 * (1e+06 / rho),
    talk = talk * (1e+06 / rho),
    oxygen = oxygen * (1e+06 / rho),
    nitrate = nitrate * (1e+06 / rho),
  #  phosphate = phosphate * (1e+06 / rho),
    silicate = silicate * (1e+06 / rho)
  )

```

# AOU calculation

```{r calc_AOU}

climatology <- climatology %>%
  mutate(
    oxygen_sat_m3 = gas_satconc(
      S = sal,
      t = temp,
      P = 1.013253,
      species = "O2"
    ),
    oxygen_sat_kg = oxygen_sat_m3 * (1e+3 / rho),
    AOU = oxygen_sat_kg - oxygen
  ) %>%
  select(-oxygen_sat_kg,-oxygen_sat_m3)

```


# Neutral density calculation

Neutral density gamma was calculated with a Python script provided by Serazin et al (2011), which performs a polynomial approximation of the original gamma calculation.

```{r calc_neutral_density, eval=FALSE}

# calculate pressure from depth
climatology <- climatology %>%
  mutate(CTDPRS = gsw_p_from_z(-depth,
                               lat))

# rename variables according to python script
climatology_gamma_prep <- climatology %>%
  rename(LATITUDE = lat,
         LONGITUDE = lon,
         SALNTY = sal)

# load python scripts
source_python(paste(
  path_functions,
  "python_scripts/Gamma_GLODAP_python.py",
  sep = ""
))

# calculate gamma
climatology_gamma_calc <-
  calculate_gamma(climatology_gamma_prep)

# reverse variable naming
climatology <- climatology_gamma_calc %>%
  select(-c(CTDPRS, THETA)) %>%
  rename(
    lat = LATITUDE,
    lon = LONGITUDE,
    sal = SALNTY,
    gamma  = GAMMA
  )

climatology <- as_tibble(climatology)

rm(climatology_gamma_calc, climatology_gamma_prep)

```

# Write file

```{r write_climatology_predictor_file, eval=FALSE}

# select relevant columns
climatology <- climatology %>%
  select(-rho)

# write csv file
climatology %>%
  write_csv(paste(path_preprocessing,
                  "climatology_runA_2007.csv",
                  sep = ""))

```


# Plots

Below, following subsets of the climatology are plotted for all relevant predictors:  

- Horizontal planes at 4 depth levels
- Global section along track indicated by white lines in maps.

```{r climatology_maps_and_sections, eval=FALSE}

# define plotting variables
vars <- c(
  "tco2",
  "talk",
  "sal",
  "nitrate",
 # "phosphate",
  "silicate",
  "oxygen",
  "temp",
  "AOU",
  "gamma"
)

# i_var <- vars[1]

for (i_var in vars) {
  # plot maps
  
  print(p_map_climatology(df = climatology,
                          var = i_var))
  
  # plot sections
  
  print(p_section_global(df = climatology,
                         var = i_var))
  
}

```
