---
title: "GLODAP subset variable climate A"
author: "Jens Daniel Müller"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  workflowr::wflow_html:
    number_sections: true
    toc_depth: 3
    toc_float:
      collapsed: false
editor_options:
  chunk_output_type: console
---

```{r parent, child = "/nfs/kryo/work/jenmueller/emlr_cant/utilities/setup.Rmd"}
# this chunk runs the code stored in setup.Rmd
# if required, please refer to instructions given here:
# https://jdblischak.github.io/workflowr/articles/wflow-07-common-code.html
```

```{r define_paths}
path_GLODAP_preprocessing <-
  paste(path_root, "/observations/preprocessing/", sep = "")

path_cmorized <-
  "/nfs/kryo/work/loher/CESM_output/RECCAP2/cmorized_March2021/split_monthly/"

path_preprocessing <-
  paste(path_root, "/model/preprocessing/", sep = "")
```

```{r load_libraries_specific, include=FALSE}
library(stars)
library(lubridate)
library(rqdatatable)
library(gsw)
library(marelac)
library(oce)
library(reticulate)
```

# Select basin mask

```{r select_basin_mask}

# use only three basin to assign general basin mask
# ie this is not specific to the MLR fitting
basinmask <- basinmask %>%
  filter(MLR_basins == "2") %>%
  select(lat, lon, basin_AIP)

```

# Read GLODAPv2_2020 preprocessed files

```{r read_GLODAPv2_2020_preprocessed_file}

GLODAP <-
  read_csv(paste(path_GLODAP_preprocessing,
                 "GLODAPv2.2021_preprocessed.csv",
                 sep = ""))

GLODAP <- GLODAP %>%
  mutate(month = month(date))

GLODAP <- GLODAP %>%
  filter(year <= 2019)

```

# Subset cmorized data according to GLODAP observation

Here we subset cmorized (1x1) data from the model with variable forcing, according to the presence of GLODAP observations in a previously cleaned file.

Besides, Model results are given in [mol m^-3^], whereas GLODAP data are in [µmol kg^-1^]. This refers to the variables:

- DIC  
- ALK  
- O2  
- NO3  
- PO4  
- SiO3
- AOU (calculated)

For comparison, model results were converted from [mol m^-3^] to [µmol kg^-1^]

```{r subset_cmorized_variable_forcing_data, eval=FALSE}

# set name of model to be subsetted
model_ID <- "A"

# for loop across years
years <- c("1982":"2019")

for (i_year in years) {
  # i_year <- years[30]
  
  # select GLODAP data for that year
  GLODAP_year <- GLODAP %>%
    filter(year == i_year)
  
  # create month x lat x lon grid of observations
  Glodap_year_grid_horizontal <- GLODAP_year %>%
    distinct(month, lat, lon)
  
  # create month x lat x lon x depth grid of observations
  Glodap_year_grid_depth <- GLODAP_year %>%
    distinct(month, lat, lon, depth)
  
  # for loop across variables
  variables <-
    c("so", "thetao", "dissic", "talk", "o2", "no3", "po4", "si")
  
  for (i_variable in variables) {
    # i_variable <- variables[1]
    
    # read list of all files
    file <-
      list.files(
        path = path_cmorized,
        pattern = paste(
          "^",
          i_variable,
          "_CESM-ETHZ_",
          model_ID,
          "_1_gr_",
          i_year,
          ".nc",
          sep = ""
        )
      )
    print(file)
    
    # read in data
    variable_data <-
      read_ncdf(paste(path_cmorized,
                      file,
                      sep = ""),
                make_units = FALSE)
    
    # convert to tibble
    variable_data_tibble <- variable_data %>%
      as_tibble()
    
    # remove open link to nc file
    rm(variable_data)
    
    # remove na values
    variable_data_tibble <-
      variable_data_tibble %>%
      filter(!is.na(!!sym(i_variable)))
    
    # harmonize longitudes
    variable_data_tibble <- variable_data_tibble %>%
      mutate(lon = if_else(lon < 20, lon + 360, lon))
    
    # only consider model grids within basinmask
    variable_data_tibble <-
      inner_join(variable_data_tibble, basinmask) %>%
      select(-basin_AIP)
    
    # mutate variables
    variable_data_tibble <- variable_data_tibble %>%
      mutate(month = month(time_mon)) %>%
      select(-time_mon)
    
    # calculate model summary stats
    stats <- variable_data_tibble %>%
      pull(!!sym(i_variable)) %>%
      summary()
    
    stats <- c(year = i_year, variable = i_variable, stats)
    
    if (exists("stats_summary")) {
      stats_summary <- bind_rows(stats_summary, stats)
    }
    
    if (!exists("stats_summary")) {
      stats_summary <- stats
    }
    
    rm(stats)
    
    # subset model at month x lat x lon grid of observations
    model_grid_horizontal <-
      inner_join(Glodap_year_grid_horizontal, variable_data_tibble)
    
    # join model and month x lat x lon x depth grid of observations
    model_obs <-
      full_join(model_grid_horizontal, Glodap_year_grid_depth)
    
    # calculate nr of observations per month x lat x lon grid
    model_obs <- model_obs %>%
      group_by(month, lat, lon) %>%
      mutate(n = sum(!is.na(!!sym(i_variable)))) %>%
      ungroup()
    
    # set variable value from model for observation depth, if only one model depth available
    model_obs_set <- model_obs %>%
      filter(n == 1) %>%
      group_by(lon, lat, month) %>%
      mutate(!!sym(i_variable) := mean(!!sym(i_variable), na.rm = TRUE)) %>%
      ungroup()
    
    # interpolate variable value from model to observation depth
    model_obs_interpo <- model_obs %>%
      filter(n > 1) %>%
      group_by(lon, lat, month) %>%
      arrange(depth) %>%
      mutate(!!sym(i_variable) := approxfun(depth, !!sym(i_variable), rule = 2)(depth)) %>%
      ungroup()
    
    # join interpolated and set model values
    model_obs_interpo <- full_join(model_obs_interpo, model_obs_set)
    rm(model_obs_set)
    
    # subsetted interpolated values at observation depth
    model_obs_interpo <-
      inner_join(Glodap_year_grid_depth, model_obs_interpo) %>%
      select(-n) %>%
      mutate(year = as.numeric(i_year))
    
    # select observation grids without corresponding model subset
    na_model <-
      full_join(Glodap_year_grid_depth, model_obs_interpo) %>%
      filter(is.na(!!sym(i_variable))) %>%
      select(month, lat, lon) %>%
      unique()
    
    # rename interpolated model variable to indicate as model output
    model_obs_interpo <- model_obs_interpo %>%
      rename(!!sym(paste(i_variable, "model", sep = "_")) := !!sym(i_variable))
    
    # add model subset to GLODAP
    GLODAP <-
      natural_join(
        GLODAP,
        model_obs_interpo,
        by = c("year", "month", "lat", "lon", "depth"),
        jointype = "FULL"
      )
    
    # calculate annual average variable
    variable_data_tibble_annual_average <- variable_data_tibble %>%
      fselect(-month) %>%
      fgroup_by(lat, lon, depth) %>% {
        add_vars(fgroup_vars(., "unique"),
                 fmean(., keep.group_vars = FALSE))
      }
    
    # select surface annual average variable
    variable_data_tibble_annual_average_surface <-
      variable_data_tibble_annual_average %>%
      filter(depth == min(depth))
    
    # surface map of variable
    map +
      geom_raster(data = variable_data_tibble_annual_average_surface,
                  aes(lon, lat, fill = !!sym(i_variable))) +
      scale_fill_viridis_c(name = i_variable) +
      geom_raster(data = model_obs_interpo,
                  aes(lon, lat), fill = "black") +
      geom_raster(data = na_model,
                  aes(lon, lat), fill = "red") +
      labs(
        title = "GLODAP-based cmorized subset distribution",
        subtitle = paste(
          "Model depth: 5m | Annual average of year",
          i_year,
          "| red = subsetting failed"
        ),
        x = "Longitude",
        y = "Latitude"
      )
    
    ggsave(
      paste(
        path_preprocessing,
        "regular_subset_distribution_runA_2021/",
        i_variable,
        "_",
        i_year,
        ".png",
        sep = ""
      ),
      width = 5,
      height = 3
    )
  }
  
}

# write raw data file for GLODAP-based subsetting model variables
GLODAP %>%
  write_csv(
    paste(
      path_preprocessing,
      "GLODAPv2.2021_preprocessed_model_runA_raw_subset.csv",
      sep = ""
    )
  )

# write file for model summary statistics (original cmorized unit)
stats_summary %>%
  write_csv(
    paste(
      path_preprocessing,
      "regular_subset_distribution_runA_2021/",
      model_ID,
      "_summary_stats.csv",
      sep = ""
    )
  )

```

```{r prepare_model_subset, eval=FALSE}


# read file for GLODAP-based subsetting model variables
GLODAP <-
  read_csv(
    paste(
      path_preprocessing,
      "GLODAPv2.2021_preprocessed_model_runA_raw_subset.csv",
      sep = ""
    ),
    col_types = cols(
      .default = col_double(),
      basin_AIP = col_character(),
      date = col_date(format = ""),
      dissic_model = col_double(),
      no3_model = col_double(),
      o2_model = col_double(),
      po4_model = col_double(),
      si_model = col_double(),
      so_model = col_double(),
      talk_model = col_double(),
      thetao_model = col_double()
    )
  )


# filter out GLODAP grids without model subset
GLODAP <- GLODAP %>%
  filter(!is.na(so_model))

# calculate model temperature
GLODAP <- GLODAP %>%
  mutate(temp_model = gsw_pt_from_t(
    SA = so_model,
    t = thetao_model,
    p = 10.1325,
    p_ref = depth
  ))

# unit conversion from mol/m3 to µmol/kg
GLODAP <- GLODAP %>%
  mutate(
    rho = gsw_pot_rho_t_exact(
      SA = so_model,
      t = temp_model,
      p = depth,
      p_ref = 10.1325
    ),
    dissic_model = dissic_model * (1e+6 / rho),
    talk_model = talk_model * (1e+6 / rho),
    o2_model = o2_model * (1e+6 / rho),
    no3_model = no3_model * (1e+6 / rho),
    po4_model = po4_model * (1e+6 / rho),
    si_model = si_model * (1e+6 / rho)
  )

# calculate AOU
GLODAP <- GLODAP %>%
  mutate(
    oxygen_sat_m3 = gas_satconc(
      S = so_model,
      t = temp_model,
      P = 1.013253,
      species = "O2"
    ),
    oxygen_sat_kg = oxygen_sat_m3 * (1e+3 / rho),
    aou_model = oxygen_sat_kg - o2_model
  ) %>%
  select(-oxygen_sat_kg, -oxygen_sat_m3)

# calculate gamma model in temporary data frame
GLODAP_gamma <- GLODAP %>%
  select(depth, lat,
         so_model, thetao_model, lon)

GLODAP_gamma <- GLODAP_gamma %>%
  mutate(CTDPRS = gsw_p_from_z(-depth,
                               lat))

GLODAP_gamma <- GLODAP_gamma %>%
  rename(
    LATITUDE = lat,
    LONGITUDE = lon,
    SALNTY = so_model,
    THETA = thetao_model
  )

source_python(
  paste(
    path_root,
    "/utilities/functions/python_scripts/",
    "Gamma_GLODAP_python.py",
    sep = ""
  )
)

GLODAP_gamma <- calculate_gamma(GLODAP_gamma)

# join gamma column with original data frame
GLODAP <- GLODAP %>%
  mutate(gamma_model = GLODAP_gamma$GAMMA)

rm(GLODAP_gamma)

# Replace model value with NA, if observations are NA
GLODAP$so_model <-
  ifelse(is.na(GLODAP$sal), NA, GLODAP$so_model)

GLODAP$thetao_model <-
  ifelse(is.na(GLODAP$theta), NA, GLODAP$thetao_model)

GLODAP$temp_model <-
  ifelse(is.na(GLODAP$temp), NA, GLODAP$temp_model)

GLODAP$dissic_model <-
  ifelse(is.na(GLODAP$tco2), NA, GLODAP$dissic_model)

GLODAP$talk_model <-
  ifelse(is.na(GLODAP$talk), NA, GLODAP$talk_model)

GLODAP$o2_model <-
  ifelse(is.na(GLODAP$oxygen), NA, GLODAP$o2_model)

GLODAP$no3_model <-
  ifelse(is.na(GLODAP$nitrate), NA, GLODAP$no3_model)

GLODAP$po4_model <-
  ifelse(is.na(GLODAP$phosphate), NA, GLODAP$po4_model)

GLODAP$si_model <-
  ifelse(is.na(GLODAP$silicate), NA, GLODAP$si_model)

GLODAP$aou_model <-
  ifelse(is.na(GLODAP$aou), NA, GLODAP$aou_model)


# write file for GLODAP observations + subsetted model variables
GLODAP %>%
  write_csv(
    paste(
      path_preprocessing,
      "GLODAPv2.2021_preprocessed_model_runA_both.csv",
      sep = ""
    )
  )

# remove GLODAP observations and rename model subset
GLODAP <- GLODAP %>%
  select(-c(
    sal,
    theta,
    temp,
    tco2,
    talk,
    oxygen,
    nitrate,
    phosphate,
    silicate,
    aou,
    gamma
  )) %>%
  rename(
    sal = so_model,
    theta = thetao_model,
    temp = temp_model,
    tco2 = dissic_model,
    talk = talk_model,
    oxygen = o2_model,
    nitrate = no3_model,
    phosphate = po4_model,
    silicate = si_model,
    aou = aou_model,
    gamma = gamma_model
  )

```

# Write files

```{r write_files, eval=FALSE}

# write final file for GLODAP-based subsetting model variables
GLODAP %>%
  select(-row_number) %>% 
  write_csv(paste(path_preprocessing,
                  "GLODAPv2.2021_preprocessed_model_runA_final.csv",
                  sep = ""))

```


# Test for interpolation

```{r test_for_interpolation}

GLODAP <-
  read_csv(paste(path_GLODAP_preprocessing,
                 "GLODAPv2.2021_preprocessed.csv",
                 sep = ""))

GLODAP <- GLODAP %>%
  mutate(month = month(date))

# select GLODAP data for 2019
GLODAP_2019 <- GLODAP %>%
  filter(year == 2019)

# create month x lat x lon grid of observations
Glodap_year_grid_horizontal <- GLODAP_2019 %>%
  select(month, lat, lon) %>%
  unique()

# create month x lat x lon x depth grid of observations
Glodap_year_grid_depth <- GLODAP_2019 %>%
  select(month, lat, lon, depth) %>%
  unique()

# read in cmorized tco2 output in year 2019
variable_data_tibble <-
  read_ncdf(paste(path_cmorized, 
    "dissic_CESM-ETHZ_A_1_gr_2019.nc",
    sep = ""
  )) %>%
  as_tibble()

# remove na values
variable_data_tibble <-
  variable_data_tibble %>%
  filter(!is.na(dissic))

# harmonize longitudes
variable_data_tibble <- variable_data_tibble %>%
  mutate(lon = if_else(lon < 20, lon + 360, lon))

# only consider model grids within basinmask
variable_data_tibble <-
  inner_join(variable_data_tibble, basinmask) %>%
  select(-basin_AIP)

# mutate variables
variable_data_tibble <- variable_data_tibble %>%
  mutate(month = month(time_mon), dissic = as.numeric(dissic)) %>%
  select(-time_mon)

# subset model at month x lat x lon grid of observations
model_grid_horizontal <-
  inner_join(Glodap_year_grid_horizontal, variable_data_tibble)

# join model and month x lat x lon x depth grid of observations
model_obs <-
  full_join(model_grid_horizontal, Glodap_year_grid_depth)

# calculate nr of observations per month x lat x lon grid
model_obs <- model_obs %>%
  group_by(month, lat, lon) %>%
  mutate(n = sum(!is.na(dissic))) %>%
  ungroup()

# interpolate variable value from model to observation depth
model_obs_interpo <- model_obs %>%
  filter(n > 1) %>%
  group_by(lon, lat, month) %>%
  arrange(month, lat, lon, depth) %>%
  mutate(dissic_interpolate = approxfun(depth, dissic, rule = 2)(depth)) %>%
  ungroup()

ggplot() +
  geom_path(
    data = model_obs_interpo %>%
      filter(lat == -47.5, lon == 306.5, !is.na(dissic), month == 4) %>%
      arrange(depth),
    aes(dissic, depth, col = "model")
  ) +
  geom_point(
    data = model_obs_interpo %>%
      filter(lat == -47.5, lon == 306.5, !is.na(dissic), month == 4) %>%
      arrange(depth),
    aes(dissic, depth, col = "model")
  ) +
  geom_point(
    data = model_obs_interpo %>%
      filter(lat == -47.5, lon == 306.5, is.na(dissic), month == 4),
    aes(dissic_interpolate, depth, col = "interpolated")
  ) +
  scale_y_reverse() +
  scale_color_brewer(palette = "Dark2", name = "") +
  labs(title = "Interpolation to sampling depth - tco2 of year 2019")

```

# Test for obs-model depth offset

```{r test_for_depth_offset}

GLODAP_max_depth <- GLODAP %>%
  select(lon, lat, depth) %>%
  group_by(lon, lat) %>%
  summarise(max_depth_GLODAP = max(depth))

model_max_depth <- variable_data_tibble %>%
  select(lon, lat, depth) %>%
  group_by(lon, lat) %>%
  summarise(max_depth_model = max(depth))

GLODAP_model_depth_offset <-
  left_join(GLODAP_max_depth, model_max_depth) %>%
  mutate(offset = max_depth_GLODAP - max_depth_model)

map +
  geom_raster(
    data = GLODAP_model_depth_offset %>% 
      filter(offset > 500),
    aes(lon, lat, fill = offset)
  ) +
  scale_fill_viridis_c(direction =  -1) +
  labs(
    title = "GLODAP-model max sampling depth offset",
    subtitle = "Year 1971 - 2019",
    x = "Longitude",
    y = "Latitude"
  )

```


# GLODAP observations vs cmorized subset comparison

```{r read_GLODAP_with_cmorized_subset_file}

GLODAP_cmorized <- read_csv(paste(path_preprocessing,
                                  "GLODAPv2.2021_preprocessed_model_runA_both.csv",
                                  sep = ""))

```

```{r GLODAP_vs_cmorized_subset_comparison}

# for loop across variables
obs_var <-
  c(
    "tco2",
    "talk",
    "oxygen",
    "aou",
    "nitrate",
    "phosphate",
    "silicate",
    "sal",
    "temp",
    "theta",
    "gamma"
  )

model_var <-
  c(
    "dissic_model",
    "talk_model",
    "o2_model",
    "aou_model",
    "no3_model",
    "po4_model",
    "si_model",
    "so_model",
    "temp_model",
    "thetao_model",
    "gamma_model"
  )

for (i in 1:11) {
#  i <- 1
  
  # select correlated observation and model variable
  GLODAP_cmorized_var <- GLODAP_cmorized %>%
    select(year,
           month,
           lat,
           lon,
           depth,
           basin_AIP,
           !!sym(obs_var[i]),
           !!sym(model_var[i])) %>%
    drop_na() %>%
    mutate(
      season = case_when(
        month %in% c(3, 4, 5) ~ "Spring",
        month %in% c(6, 7, 8) ~ "Summer",
        month %in% c(9, 10, 11) ~ "Autumn",
        month %in% c(12, 1, 2) ~ "Winter"
      )
    )
  
  # calculate equal axis limits and binwidth
  axis_lims <- GLODAP_cmorized_var %>%
    summarise(max_value = max(c(max(!!sym(
      obs_var[i]
    )),
    max(
      !!sym(model_var[i])
    ))),
    min_value = min(c(min(!!sym(
      obs_var[i]
    )),
    min(
      !!sym(model_var[i])
    ))))
  
  binwidth_value <- (axis_lims$max_value - axis_lims$min_value) / 40
  axis_lims <- c(axis_lims$min_value, axis_lims$max_value)
  
  # obs-model plot (season)
  print(
    ggplot(GLODAP_cmorized_var, aes(
      x = !!sym(obs_var[i]),
      y = !!sym(model_var[i])
    )) +
      geom_bin2d(binwidth = binwidth_value) +
      labs(title = "Observation (x) vs Model (y)",
           subtitle = "Seasonal comparison") +
      scale_fill_viridis_c(trans = "log10") +
      geom_abline(slope = 1,
                  col = 'red') +
      coord_equal(xlim = axis_lims,
                  ylim = axis_lims) +
      facet_wrap( ~ season)
  )
  
  # obs-model plot (year)
  print(
    ggplot(GLODAP_cmorized_var, aes(
      x = !!sym(obs_var[i]),
      y = !!sym(model_var[i])
    )) +
      geom_bin2d(binwidth = binwidth_value) +
      labs(title = "Observation (x) vs Model (y)",
           subtitle = "All years") +
      scale_fill_viridis_c(trans = "log10") +
      geom_abline(slope = 1, col = 'red') +
      coord_equal(xlim = axis_lims,
                  ylim = axis_lims)
  )
  
  
  # Calculate variable offset
  GLODAP_cmorized_var <- GLODAP_cmorized_var %>%
    mutate(offset = !!sym(model_var[i]) -!!sym(obs_var[i]))
  
  # Calculate annual mean offset
  GLODAP_cmorized_var_year <- GLODAP_cmorized_var %>%
    group_by(year) %>%
    summarise(offset = mean(offset)) %>%
    ungroup()
  
  # plot annual mean offset
  print(
    GLODAP_cmorized_var_year %>%
      ggplot(aes(year, offset)) +
      geom_point() +
      geom_line() +
      labs(title = "Annual mean offset",
           subtitle = paste(sym(model_var[i]), "-", sym(obs_var[i])))
  )
  
  # spatial distribution of the model-observations offset for 4 depth intervals
  intervals <- c(0, 150, 500, 2000, 8000)
  for (j in 1:4) {
    # j <- 1
    GLODAP_cmorized_var_grid <- GLODAP_cmorized_var %>%
      filter(depth >= intervals[j],
             depth < intervals[j + 1]) %>%
      group_by(lat, lon) %>%
      summarise(offset = mean(offset)) %>%
      ungroup()
    
    # plot mean spatial distribution (model - obs)
    limit <-
      quantile(abs(GLODAP_cmorized_var_grid$offset), 0.98) * c(-1, 1)
    print(
      map +
        geom_raster(data = GLODAP_cmorized_var_grid, aes(lon, lat, fill = offset)) +
        scale_fill_scico(
          palette = "vik",
          name = "offset",
          limit = limit,
          na.value = "red"
        ) +
        coord_quickmap(expand = 0) +
        labs(
          title = paste(model_var[i],
                        "-",
                        obs_var[i],
                        " | mean offset per grid cell"),
          subtitle = paste(
            "Depth interval:",
            intervals[j],
            "-",
            intervals[j + 1],
            "m | red: outside 98th percentile"
          ),
          x = "Longitude",
          y = "Latitude"
        )
    )
    
    print(
      GLODAP_cmorized_var_grid %>%
        ggplot(aes(offset)) +
        geom_vline(xintercept = limit) +
        geom_histogram() +
        labs(
          title = paste(
            model_var[i],
            " - ",
            obs_var[i],
            "mean offset per grid cell | histogram + abs. 98th Percentile"
          ),
          subtitle = paste("Depth interval:",
                           intervals[j], "-", intervals[j + 1], "m")
        ) +
        coord_cartesian(expand = FALSE)
    )
  }
  
  # zonal mean section of the model-observations offset for each basin
  for (i_basin_AIP in unique(GLODAP_cmorized_var$basin_AIP)) {
   # i_basin_AIP = "Atlantic"
    GLODAP_cmorized_var_zonal <- GLODAP_cmorized_var %>%
      filter(basin_AIP == i_basin_AIP) %>%
      group_by(lat, depth) %>%
      summarise(offset = mean(offset, na.rm=TRUE)) %>%
      ungroup()
    
    # plot zonal mean section (model - obs)
    lat_max <- params_global$lat_max
    lat_min <- params_global$lat_min
    limit <-
      quantile(abs(GLODAP_cmorized_var_zonal$offset), 0.98) * c(-1, 1)
    
    print(
      GLODAP_cmorized_var_zonal %>%
        ggplot(aes(lat, depth, z = offset)) +
        stat_summary_2d(binwidth = c(1,100)) +
        scale_fill_scico(
          palette = "vik",
          name = "offset",
          limit = limit,
          na.value = "red"
        ) +
        coord_cartesian(expand = 0,
                        xlim = c(lat_min, lat_max)) +
        scale_y_reverse() +
        labs(
          title = paste(model_var[i],
                        "-",
                        obs_var[i],
                        " | zonal mean offset"),
          subtitle = paste("Basin:",
                           i_basin_AIP),
          x = "Latitude",
          y = "Depth"
        )
    )
  }
}

```
