---
title: "GLODAP based subset"
author: "Jens Daniel Müller"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  workflowr::wflow_html:
    number_sections: true
    toc_depth: 3
    toc_float:
      collapsed: false
editor_options:
  chunk_output_type: console
---

```{r parent, child = "/nfs/kryo/work/jenmueller/emlr_cant/utilities/setup.Rmd"}
# this chunk runs the code stored in setup.Rmd
# if required, please refer to instructions given here:
# https://jdblischak.github.io/workflowr/articles/wflow-07-common-code.html
```

```{r define_paths}
path_GLODAP_preprocessing <-
  paste(path_root, "/observations/preprocessing/", sep = "")
path_cmorized <-
  "/nfs/kryo/work/loher/CESM_output/RECCAP2/cmorized_Dec2020/split_monthly/"
path_preprocessing <-
  paste(path_root, "/model/preprocessing/", sep = "")
```

```{r load_libraries_specific, include=FALSE}
library(stars)
library(lubridate)
library(rqdatatable)
library(gsw)
library(marelac)
```

# Select basin mask

```{r select_basin_mask}

# use only three basin to assign general basin mask
# ie this is not specific to the MLR fitting
basinmask <- basinmask %>%
  filter(MLR_basins == "2") %>%
  select(lat, lon, basin_AIP)

```

# Read GLODAPv2_2020 preprocessed files

```{r read_GLODAPv2_2020_preprocessed_file}

GLODAP <-
  read_csv(paste(path_GLODAP_preprocessing,
                 "GLODAPv2.2020_preprocessed.csv",
                 sep = ""))
GLODAP <- GLODAP %>%
  mutate(month = month(date))

```

# Subset cmorized data according to GLODAP observation

Here we subset cmorized (1x1) data from the model with variable forcing, according to the presence of GLODAP observations in a previously cleaned file.

Simultaneously, we calculate annual model summary statistics and annual average DIC fields.

Besides, Model results are given in [mol m^-3^], whereas GLODAP data are in [µmol kg^-1^]. This refers to the variables:

- DIC  
- ALK  
- O2  
- NO3  
- PO4  
- SiO3
- AOU (calculated)

For comparison, model results were converted from [mol m^-3^] to [µmol kg^-1^]

```{r subset_cmorized_variable_forcing_data, eval=FALSE}

# set name of model to be subsetted
model_ID <- "A"

# for loop across years
years <- c("1982":"2019")

for (i_year in years) {
  # for manual testing
  #i_year <- years[1]
  
  # select GLODAP data for that year
  GLODAP_year <- GLODAP %>%
    filter(year == i_year)
  
  # create month x lat x lon grid of observations
  grid_subset <- GLODAP_year %>%
    select(month, lat, lon) %>%
    unique()
  
  # create month x lat x lon x depth grid of observations
  obs_depth <- GLODAP_year %>%
    select(month, lat, lon, depth) %>%
    unique()
  
  # for loop across variables
  variables <-
    c("so", "thetao", "dissic", "talk", "o2", "no3", "po4", "si")
  # "SALT", "TEMP", "DIC", "ALK", "O2", "NO3", "PO4", "SiO3"
  
  for (i_variable in variables) {
    # Uncomment line below for manual testing
    #i_variable <- variables[1]
    
    # read list of all files
    file <-
      list.files(
        path = path_cmorized,
        pattern = paste(
          "^",
          i_variable,
          "_CESM-ETHZ_",
          model_ID,
          "_1_gr_",
          i_year,
          ".nc",
          sep = ""
        )
      )
    print(file)
    
    # read in data
    variable_data <-
      read_ncdf(paste(path_cmorized,
                      file,
                      sep = ""))
    
    # convert to tibble
    variable_data_tibble <- variable_data %>%
      as_tibble()
    
    # remove open link to nc file
    rm(variable_data)
    
    # remove na values -> do this early, to speed up subsequent tasks
    variable_data_tibble <-
      variable_data_tibble %>%
      filter(!is.na(!!sym(i_variable)))
    
    # convert longitudes
    variable_data_tibble <- variable_data_tibble %>%
      mutate(lon = if_else(lon < 20, lon + 360, lon))
    
    # only consider model grids within basinmask
    variable_data_tibble <-
      inner_join(variable_data_tibble, basinmask) %>%
      select(-basin_AIP)
    
    # mutate variables
    variable_data_tibble <- variable_data_tibble %>%
      mutate(month = month(time_mon),!!sym(i_variable) := as.numeric(!!sym(i_variable))) %>%
      select(-time_mon)
    
    # calculate model summary stats
    stats <- variable_data_tibble %>%
      pull(!!sym(i_variable)) %>%
      summary()
    
    stats <- c(year = i_year, variable = i_variable, stats)
    
    if (exists("stats_summary")) {
      stats_summary <- bind_rows(stats_summary, stats)
    }
    
    if (!exists("stats_summary")) {
      stats_summary <- stats
    }
    
    rm(stats)
    
    # subset model at month x lat x lon grid of observations
    model_subset <-
      inner_join(grid_subset, variable_data_tibble)
    
    # join model and month x lat x lon x depth grid of observations
    model_obs <- full_join(model_subset, obs_depth)
    
    # calculate nr of observations per month x lat x lon grid
    model_obs <- model_obs %>%
      group_by(month, lat, lon) %>%
      mutate(n = sum(!is.na(!!sym(i_variable)))) %>%
      ungroup()
    
    # interpolate variable value from model to observation depth
    model_obs_interpo <- model_obs %>%
      filter(n > 1) %>%
      group_by(lon, lat, month) %>%
      arrange(depth) %>%
      mutate(!!sym(i_variable) := approxfun(depth, !!sym(i_variable), rule = 2)(depth)) %>%
      ungroup()
    
    # subsetted interpolated values at observation depth
    model_obs_interpo <-
      inner_join(obs_depth, model_obs_interpo) %>%
      select(-n) %>%
      mutate(year = as.numeric(i_year))
    
    # select observation grids without corresponding model subset
    na_model <- full_join(obs_depth, model_obs_interpo) %>%
      filter(is.na(!!sym(i_variable))) %>%
      select(month, lat, lon) %>%
      unique()
    
    # rename interpolated model variable to indicate as model output
    model_obs_interpo <- model_obs_interpo %>%
      rename(!!sym(paste(i_variable, "model", sep = "_")) := !!sym(i_variable))
    
    # add model subset to GLODAP
    GLODAP <-
      natural_join(
        GLODAP,
        model_obs_interpo,
        by = c("year", "month", "lat", "lon", "depth"),
        jointype = "FULL"
      )
    
    # calculate annual average variable
    variable_data_tibble_annual_average <- variable_data_tibble %>%
      fselect(-month) %>%
      fgroup_by(lat, lon, depth) %>% {
        add_vars(fgroup_vars(., "unique"),
                 fmean(., keep.group_vars = FALSE))
      }
    
    # select surface annual average variable
    variable_data_tibble_annual_average_surface <-
      variable_data_tibble_annual_average %>%
      filter(depth == min(depth))
    
    # surface map of variable
    map +
      geom_raster(data = variable_data_tibble_annual_average_surface, aes(lon, lat, fill = !!sym(i_variable))) +
      scale_fill_viridis_c(name = i_variable) +
      coord_quickmap(expand = 0) +
      geom_point(data = model_obs_interpo,
                 aes(lon, lat)) +
      geom_point(data = na_model,
                 aes(lon, lat), colour = "red") +
      labs(
        title = "GLODAP-based cmorized subset distribution",
        subtitle = paste("Model depth: 5m | Annual average of year", i_year),
        x = "Longitude",
        y = "Latitude"
      )
    
    ggsave(
      paste(
        path_preprocessing,
        "regular_subset_distribution/",
        i_variable,
        "_",
        i_year,
        ".png",
        sep = ""
      ),
      width = 5,
      height = 3
    )
    # GLODAP with model subset: black
    # GLODAP without model subset: red
  }
  
}

# filter out GLODAP grids without model subset
GLODAP <- GLODAP %>%
  filter(!is.na(so_model))

# calculate model temperature
GLODAP <- GLODAP %>%
  mutate(temp_model = gsw_pt_from_t(
    SA = so_model,
    t = thetao_model,
    p = 10.1325,
    p_ref = depth
  ))

# unit transfer from mol/m3 to µmol/kg
GLODAP <- GLODAP %>%
  mutate(
    rho = gsw_pot_rho_t_exact(
      SA = so_model,
      t = temp_model,
      p = depth,
      p_ref = 10.1325
    ),
    dissic_model = dissic_model * (1000000 / rho),
    talk_model = talk_model * (1000000 / rho),
    o2_model = o2_model * (1000000 / rho),
    no3_model = no3_model * (1000000 / rho),
    po4_model = po4_model * (1000000 / rho),
    si_model = si_model * (1000000 / rho)
  )

# calculate AOU
GLODAP <- GLODAP %>%
  mutate(
    oxygen_sat_m3 = gas_satconc(
      S = so_model,
      t = temp_model,
      P = 1.013253,
      species = "O2"
    ),
    oxygen_sat_kg = oxygen_sat_m3 * (1000 / rho),
    aou_model = oxygen_sat_kg - o2_model
  ) %>%
  select(-oxygen_sat_kg, -oxygen_sat_m3)

# write file for GLODAP observations + subsetted model variables
GLODAP %>%
  write_csv(paste(path_preprocessing,
                  "GLODAP_with_cmorized_subset.csv",
                  sep = ""))

# mutate Nan for var -> var_model
GLODAP$so_model <- ifelse(is.na(GLODAP$sal), NA, GLODAP$so_model)
GLODAP$thetao_model <-
  ifelse(is.na(GLODAP$theta), NA, GLODAP$thetao_model)
GLODAP$temp_model <-
  ifelse(is.na(GLODAP$temp), NA, GLODAP$temp_model)
GLODAP$dissic_model <-
  ifelse(is.na(GLODAP$tco2), NA, GLODAP$dissic_model)
GLODAP$talk_model <-
  ifelse(is.na(GLODAP$talk), NA, GLODAP$talk_model)
GLODAP$o2_model <- ifelse(is.na(GLODAP$oxygen), NA, GLODAP$o2_model)
GLODAP$no3_model <-
  ifelse(is.na(GLODAP$nitrate), NA, GLODAP$no3_model)
GLODAP$po4_model <-
  ifelse(is.na(GLODAP$phosphate), NA, GLODAP$po4_model)
GLODAP$si_model <-
  ifelse(is.na(GLODAP$silicate), NA, GLODAP$si_model)
GLODAP$aou_model <- ifelse(is.na(GLODAP$aou), NA, GLODAP$aou_model)

# remove GLODAP observations and rename model subset
GLODAP <- GLODAP %>%
  select(-c(
    sal,
    theta,
    temp,
    tco2,
    talk,
    oxygen,
    nitrate,
    phosphate,
    silicate,
    aou
  )) %>%
  rename(
    sal = so_model,
    theta = thetao_model,
    temp = temp_model,
    tco2 = dissic_model,
    talk = talk_model,
    oxygen = o2_model,
    nitrate = no3_model,
    phosphate = po4_model,
    silicate = si_model,
    aou = aou_model
  )

# write file for GLODAP-based subsetting model variables
GLODAP %>%
  write_csv(paste(path_preprocessing,
                  "original_subset.csv",
                  sep = ""))

# write file for model summary statistics (original cmorized unit)
stats_summary %>%
  write_csv(
    paste(
      path_preprocessing,
      "regular_subset_distribution/",
      model_ID,
      "_summary_stats.csv",
      sep = ""
    )
  )

```


## Write file
 
```{r write_clean_data_files, eval=FALSE}

GLODAP %>% write_csv(paste(path_preprocessing,
                           "GLODAPv2.2020_preprocessed.csv",
                           sep = ""))

```

# Test for interpolation

```{r test_for_interpolation, eval=FALSE}

# subset model at month x lat x lon grid of observations
model_subset <-
  inner_join(grid_subset, variable_data_tibble)

# join model and month x lat x lon x depth grid of observations
model_obs <- full_join(model_subset, obs_depth)

# calculate nr of observations per month x lat x lon grid
model_obs <- model_obs %>%
  group_by(month, lat, lon) %>%
  mutate(n = sum(!is.na(!!sym(i_variable)))) %>%
  ungroup()

# interpolate variable value from model to observation depth
model_obs_interpo <- model_obs %>%
  filter(n > 1) %>%
  group_by(lon, lat, month) %>%
  arrange(month, lat, lon, depth) %>%
  mutate(!!sym(paste(i_variable, "interpolate", sep = "_")) := approxfun(depth, !!sym(i_variable), rule = 2)(depth)) %>%
  ungroup()

ggplot() +
  geom_path(
    data = model_obs_interpo %>%
      filter(lat == -48.5, lon == 305.5, !is.na(!!sym(i_variable)), month == 4) %>%
      arrange(depth),
    aes(!!sym(i_variable), depth, col = "model")
  ) +
  geom_point(
    data = model_obs_interpo %>%
      filter(lat == -48.5, lon == 305.5, month == 4),
    aes(!!sym(
      paste(i_variable, "interpolate", sep = "_")
    ), depth, col = "interpolated")
  ) +
  geom_point(
    data = model_obs_interpo %>%
      filter(lat == -48.5, lon == 305.5, !is.na(!!sym(i_variable)), month == 4) %>%
      arrange(depth),
    aes(!!sym(i_variable), depth, col = "model")
  ) +
  scale_y_reverse() +
  scale_color_brewer(palette = "Dark2", name = "") +
  labs(title = paste("Interpolation to sampling depth -", i_variable, "of year", i_year))

```
