---
title: "GLODAP subset variable climate A"
author: "Jens Daniel Müller"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  workflowr::wflow_html:
    number_sections: true
    toc_depth: 3
    toc_float:
      collapsed: false
editor_options:
  chunk_output_type: console
---

```{r parent, child = "/nfs/kryo/work/jenmueller/emlr_cant/utilities/setup.Rmd"}
# this chunk runs the code stored in setup.Rmd
# if required, please refer to instructions given here:
# https://jdblischak.github.io/workflowr/articles/wflow-07-common-code.html
```

```{r define_paths}

path_GLODAP_preprocessing <-
  paste(path_root, "/observations/preprocessing/", sep = "")

path_cmorized <-
  "/nfs/kryo/work/updata/reccap2/Models/3D_ALL/"

path_preprocessing <-
  paste0(path_root, "/model/preprocessing/GLODAP_subset_A_all_models/")
```

```{r load_libraries_specific, include=FALSE}
library(stars)
library(lubridate)
library(rqdatatable)
library(gsw)
library(marelac)
library(oce)
library(reticulate)
library(seacarb)
library(khroma)
library(colorspace)
```

# Select basin mask

```{r select_basin_mask}

# use only three basin to assign general basin mask
# ie this is not specific to the MLR fitting
basinmask <- basinmask %>%
  filter(MLR_basins == "2") %>%
  select(lat, lon, basin_AIP)

```

# Read GLODAPv2_2021 preprocessed files

```{r read_GLODAPv2_2021_preprocessed_file}

GLODAP <-
  read_csv(paste(path_GLODAP_preprocessing,
                 "GLODAPv2.2021_preprocessed.csv",
                 sep = ""))

GLODAP <- GLODAP %>%
  mutate(month = month(date))

GLODAP <- GLODAP %>%
  filter(year <= 2019)

```

# Subset cmorized data according to GLODAP observation

Here we subset cmorized (1x1) data from the model with variable forcing, according to the presence of GLODAP observations in a previously cleaned file.

Besides, Model results are given in [mol m^-3^], whereas GLODAP data are in [µmol kg^-1^]. This refers to the variables:

- DIC  
- ALK  
- O2  
- NO3  
- PO4  
- SiO3
- AOU (calculated)

For comparison, model results were converted from [mol m^-3^] to [µmol kg^-1^]

```{r create_list_of_models}

# set name of model to be subsetted
model_ID <- "A"

# for loop across variables
variables <-
  c("so", "thetao", "dissic", "talk", "o2", "no3", "po4", "si")


models <- list.files(path_cmorized)

models <-
  models[!str_detect(models, pattern = "\\.t|\\.z")]

models <-
  models[str_detect(
    models,
    pattern = c(
      "CESM|CNRM|EC-Earth3|FESOM_REcoM_LR|MOM6-Princeton|MRI-ESM2-1|NorESM-OC1.2|ORCA025-GEOMAR|ORCA1-LIM3-PISCES|planktom12"
    )
  )]


```




```{r subset_cmorized_variable_forcing_data}

# models <- models[c(2,8)]

for (i_model in models) {
  # i_model <- models[8]
  print(i_model)
  
  variables_available <-
    list.files(path = paste0(path_cmorized, i_model),
               pattern = paste0("_", model_ID, "_"))
  
  variables_available <-
    str_split(variables_available,
              pattern = "_",
              simplify = TRUE)[, 1]
  variables_available <-
    variables_available[variables_available %in% variables]
  variables_available <- unique(variables_available)
  
  GLODAP_joined <- GLODAP
  
  for (i_variable in variables_available) {
    # i_variable <- variables_available[1]
    
    # read list of all files
    file <-
      list.files(path = paste0(path_cmorized, i_model),
                 pattern = paste0(i_variable, "_"))
    
    file <-
      file[str_detect(file, pattern = paste0("_", model_ID, "_"))]
    
    print(file)
    
    # read in data
    if (i_model == "NorESM-OC1.2_3D_ALL_v20211125") {
      variable_data <-
        tidync::tidync(paste(paste0(path_cmorized, i_model),
                             file,
                             sep = "/")) %>%
        tidync::hyper_tibble() %>% 
        mutate(time = as.Date(time, origin = "1980-01-01"))
    } else if (i_model %in% c("EC-Earth3_3D_ALL_v20220323",
                            "CNRM-ESM2-1_3D_ALL_v20211208")) {
      variable_data <-
        read_ncdf(paste(paste0(path_cmorized, i_model),
                        file,
                        sep = "/"),
                  make_units = FALSE,
                  make_time = FALSE)
    } else if (i_model %in% c("ORCA025-GEOMAR_3D_ALL_v20210804")) {
      
      for (i_file in file) {
        # i_file <- file[1]
        
        temp <-
          read_ncdf(paste(paste0(path_cmorized, i_model),
                          i_file,
                          sep = "/"),
                    make_units = FALSE)

        temp_dates <-
          read_stars(paste(paste0(path_cmorized, i_model),
                          i_file,
                          sep = "/"),
                    make_units = FALSE)
          
        temp_dates <- st_get_dimension_values(temp_dates, "time")
        
        temp <-
          st_set_dimensions(temp,
                            "time",
                            values = temp_dates)

        if (exists("variable_data")) {
          variable_data <- c(variable_data, temp)
        }
        
        if (!exists("variable_data")) {
          variable_data <- temp
        }
        rm(temp, temp_dates)
        
      }
      
      
    } else {
      variable_data <-
        read_ncdf(paste(paste0(path_cmorized, i_model),
                        file,
                        sep = "/"),
                  make_units = FALSE)
    }
    
    
    
    if (i_model == "CNRM-ESM2-1_3D_ALL_v20211208") {
      CNRM_depth <-
        read_ncdf(
          paste(
            paste0(path_cmorized, i_model),
            "depth_CNRM-ESM2-1_1_gr_1980-2018_v20211208.nc",
            sep = "/"
          ),
          make_units = FALSE,
          make_time = FALSE
        ) %>%
        as_tibble()
      
      CNRM_depth <- CNRM_depth %>%
        distinct(lev) %>% 
        arrange(lev) %>% 
        rename(depth = lev) %>% 
        pull()
      
      variable_data <-
        st_set_dimensions(variable_data,
                          "lev",
                          values = CNRM_depth,
                          names = "depth")

      variable_data <-
        st_set_dimensions(variable_data,
                          "time",
                          values = ymd(1980:2018, truncated = 2L))
      
      # CNRM_depth %>%
      #   slice_sample(n = 1e4) %>%
      #   ggplot(aes(lev, depth)) +
      #   geom_point(alpha = 0.3) +
      #   labs(title = "depth_CNRM-ESM2-1_1_gr_1980-2018_v20211208.nc",
      #        subtitle = "random sample of 1000 data points")
      # 
      # CNRM_depth %>%
      #   filter(lev == unique(CNRM_depth$lev)[70]) %>%
      #   ggplot(aes(lon, lat, fill = depth)) +
      #   geom_tile() +
      #   scale_fill_viridis_c(direction = -1) +
      #   coord_quickmap(expand = 0) +
      #   labs(title = "depth_CNRM-ESM2-1_1_gr_1980-2018_v20211208.nc",
      #        subtitle = "lev == 4787.702 (position 70)")
      
    }
    
    # convert to tibble
    variable_data_tibble <- variable_data %>%
      as_tibble()
    
    # remove open link to nc file
    rm(variable_data)
    
    # remove na values
    variable_data_tibble <-
      variable_data_tibble %>%
      filter(!is.na(!!sym(i_variable)))
    
    if (i_model == "CESM-ETHZ_3D_ALL_v20211122") {
      variable_data_tibble <- variable_data_tibble %>%
        rename(time = time_ann)
    }

    if (i_model == "EC-Earth3_3D_ALL_v20220323") {
      variable_data_tibble <- variable_data_tibble %>%
        mutate(time = as.Date(time, origin = "1850-06-01"))
    }
    
    if (i_model == "FESOM_REcoM_LR_3D_all_v20211119") {
      variable_data_tibble <- variable_data_tibble %>%
        rename(
          lat = Lat,
          lon = Lon,
          depth = Depth,
          time = Time
        ) %>%
        mutate(time = as.Date(time, origin = '1980-01-01'))
    }
    
    if (i_model == "MOM6-Princeton_3D_ALL_v20220125") {
      variable_data_tibble <- variable_data_tibble %>%
        rename(depth = z_l)
    }
    
    if (i_model == "MRI-ESM2-1_3D_ALL_v20220502") {
      variable_data_tibble <- variable_data_tibble %>%
        rename(depth = lev)
    }
    
    
    if (i_model == "planktom12_3d_all_v20220404") {
      variable_data_tibble <- variable_data_tibble %>%
        rename(lon = LONGITUDE,
               lat = LATITUDE,
               depth = DEPTH,
               time = TIME)
    }
    
    
    # harmonize longitudes
    variable_data_tibble <- variable_data_tibble %>%
      mutate(lon = if_else(lon < 20, lon + 360, lon))
    
    # only consider model grids within basinmask
    variable_data_tibble <-
      inner_join(variable_data_tibble, basinmask) %>%
      select(-basin_AIP)
    
    # mutate variables
    variable_data_tibble <- variable_data_tibble %>%
      mutate(year = year(time)) %>%
      select(-time)
    
    
    if (i_model == "MRI-ESM2-1_3D_ALL_v20220502" &
        i_variable == "si") {
      variable_data_tibble <-
        crossing(variable_data_tibble %>%
                   select(-year),
                 year = seq(1980, 2018, 1))
    }

    if (i_model == "planktom12_3d_all_v20220404" &
        i_variable == "po4") {
      variable_data_tibble <-
        variable_data_tibble %>%
        mutate(po4 = po4 / 100)
    }
    
    # for loop across years
    years <- unique(variable_data_tibble$year)
    years <- years[years %in% (unique(GLODAP$year))]

    
    for (i_year in years) {
      # i_year <- years[1]
      print(i_year)
      
      # select GLODAP data for that year
      GLODAP_year <- GLODAP %>%
        filter(year == i_year)
      
      # create lat x lon grid of observations
      Glodap_year_grid_horizontal <- GLODAP_year %>%
        distinct(lat, lon)
      
      # create lat x lon x depth grid of observations
      Glodap_year_grid_depth <- GLODAP_year %>%
        distinct(lat, lon, depth)
      
      # select GLODAP data for that year
      variable_data_tibble_year <- variable_data_tibble %>%
        filter(year == i_year)
      
      # calculate model summary stats
      stats <- variable_data_tibble_year %>%
        pull(!!sym(i_variable)) %>%
        summary()
      
      stats <- c(year = i_year, variable = i_variable, stats)
      
      if (exists("stats_summary")) {
        stats_summary <- bind_rows(stats_summary, stats)
      }
      
      if (!exists("stats_summary")) {
        stats_summary <- stats
      }
      
      rm(stats)
      
      # subset model at lat x lon grid of observations
      model_grid_horizontal <-
        inner_join(Glodap_year_grid_horizontal,
                   variable_data_tibble_year)
      
      # join model and lat x lon x depth grid of observations
      model_obs <-
        full_join(model_grid_horizontal, Glodap_year_grid_depth)
      
      # calculate nr of observations per lat x lon grid
      model_obs <- model_obs %>%
        group_by(lat, lon) %>%
        mutate(n = sum(!is.na(!!sym(i_variable)))) %>%
        ungroup()
      
      # set variable value from model for observation depth, if only one model depth available
      model_obs_set <- model_obs %>%
        filter(n == 1) %>%
        group_by(lon, lat) %>%
        mutate(!!sym(i_variable) := mean(!!sym(i_variable), na.rm = TRUE)) %>%
        ungroup()
      
      # interpolate variable value from model to observation depth
      model_obs_interpo <- model_obs %>%
        filter(n > 1) %>%
        group_by(lon, lat) %>%
        arrange(depth) %>%
        mutate(!!sym(i_variable) := approxfun(depth, !!sym(i_variable), rule = 2)(depth)) %>%
        ungroup()
      
      # join interpolated and set model values
      model_obs_interpo <-
        full_join(model_obs_interpo, model_obs_set)
      rm(model_obs_set)
      
      # subsetted interpolated values at observation depth
      model_obs_interpo <-
        inner_join(Glodap_year_grid_depth, model_obs_interpo) %>%
        select(-n) %>%
        mutate(year = as.numeric(i_year))
      
      # select observation grids without corresponding model subset
      na_model <-
        full_join(Glodap_year_grid_depth, model_obs_interpo) %>%
        filter(is.na(!!sym(i_variable))) %>%
        select(year, lat, lon) %>%
        unique()
      
      # rename interpolated model variable to indicate as model output
      model_obs_interpo <- model_obs_interpo %>%
        rename(!!sym(paste(i_variable, "model", sep = "_")) := !!sym(i_variable))
      
      # add model subset to GLODAP
      GLODAP_joined <-
        natural_join(
          GLODAP_joined,
          model_obs_interpo,
          by = c("year", "lat", "lon", "depth"),
          jointype = "FULL"
        )
      
      # select surface annual average variable
      variable_data_tibble_year_surface <-
        variable_data_tibble_year %>%
        filter(depth == min(depth))
      
      # surface map of variable
      p_map <- map +
        geom_raster(data = variable_data_tibble_year_surface,
                    aes(lon, lat, fill = !!sym(i_variable))) +
        scale_fill_viridis_c(name = i_variable) +
        geom_tile(data = model_obs_interpo,
                    aes(lon, lat, width = 1, height = 1), fill = "black") +
        labs(
          title = "GLODAP-based cmorized subset distribution",
          subtitle = paste(
            "Model depth: 5m | Annual average of year",
            i_year,
            "| red = subsetting failed"
          ),
          x = "Longitude",
          y = "Latitude"
        )
      
      if (nrow(na_model) > 0){
      p_map <- p_map +
        geom_tile(data = na_model,
                    aes(lon, lat, width = 1, height = 1), fill = "red")
      }
      
      p_map
      
      ggsave(
        paste(
          path_preprocessing,
          "regular_subset_distribution_runA_2021/",
          str_remove(i_model, "3D_ALL_|3D_all_|3d_all_"),
          "_",
          i_variable,
          "_",
          i_year,
          ".png",
          sep = ""
        ),
        width = 5,
        height = 3
      )
    }
    
  }
  
  if (i_model == "FESOM_REcoM_LR_3D_all_v20211119") {
    GLODAP_joined <- GLODAP_joined %>% 
      mutate(po4_model = no3_model/16)
  }
  
  if (i_model == "planktom12_3d_all_v20220404") {
    GLODAP_joined <- GLODAP_joined %>% 
      mutate(no3_model = po4_model*16)
  }
  
  # Remove 3D_all from model name
  i_model <- str_remove(i_model, "3D_ALL_|3D_all_|3d_all_")
  
  # write raw data file for GLODAP-based subsetting model variables
  GLODAP_joined %>%
    write_csv(paste(
      path_preprocessing,
      paste(
        i_model,
        "GLODAPv2.2021_preprocessed_model_runA_raw_subset_ann.csv",
        sep = "_"
      ),
      sep = ""
    ))
  
  rm(GLODAP_joined)
  
  # write file for model summary statistics (original cmorized unit)
  stats_summary %>%
    write_csv(
      paste(
        path_preprocessing,
        "regular_subset_distribution_runA_2021/",
        i_model,
        "_",
        model_ID,
        "_summary_stats.csv",
        sep = ""
      )
    )
  
  
}

```

```{r prepare_model_subset}

rm(GLODAP, GLODAP_joined)

for (i_model in models) {
  # i_model <- models[3]
  
  # Remove 3D_all from model name
  i_model <- str_remove(i_model, "3D_ALL_|3D_all_|3d_all_")
  
  # read file for GLODAP-based subsetting model variables
  GLODAP_single <-
    read_csv(
      paste0(
        path_preprocessing,
        i_model,
        "_GLODAPv2.2021_preprocessed_model_runA_raw_subset_ann.csv"
      ),
      col_types = cols(
        .default = col_double(),
        basin_AIP = col_character(),
        date = col_date(format = ""),
        dissic_model = col_double(),
        no3_model = col_double(),
        o2_model = col_double(),
        po4_model = col_double(),
        si_model = col_double(),
        so_model = col_double(),
        talk_model = col_double(),
        thetao_model = col_double()
      )
    )
  
  GLODAP_single <- GLODAP_single %>% 
    mutate(model = i_model)
  
  if (exists("GLODAP")) {
    GLODAP <- bind_rows(GLODAP, GLODAP_single)
  }
  
  if (!exists("GLODAP")) {
    GLODAP <- GLODAP_single
  }
  
}

rm(GLODAP_single)

# GLODAP <- GLODAP %>%
#   sample_n(10000)

# filter out GLODAP grids without model subset
GLODAP <- GLODAP %>%
  filter(!is.na(so_model))

# calculate model temperature
GLODAP <- GLODAP %>%
  mutate(temp_model = gsw_pt_from_t(
    SA = so_model,
    t = thetao_model,
    p = 10.1325,
    p_ref = depth
  ))

# unit conversion from mol/m3 to µmol/kg
GLODAP <- GLODAP %>%
  mutate(
    rho = gsw_pot_rho_t_exact(
      SA = so_model,
      t = temp_model,
      p = depth,
      p_ref = 10.1325
    ),
    dissic_model = dissic_model * (1e+6 / rho),
    talk_model = talk_model * (1e+6 / rho),
    o2_model = o2_model * (1e+6 / rho),
    no3_model = no3_model * (1e+6 / rho),
    po4_model = po4_model * (1e+6 / rho),
    si_model = si_model * (1e+6 / rho)
  )

# calculate AOU
GLODAP <- GLODAP %>%
  mutate(
    oxygen_sat_m3 = gas_satconc(
      S = so_model,
      t = temp_model,
      P = 1.013253,
      species = "O2"
    ),
    oxygen_sat_kg = oxygen_sat_m3 * (1e+3 / rho),
    aou_model = oxygen_sat_kg - o2_model
  ) %>%
  select(-oxygen_sat_kg, -oxygen_sat_m3)

# calculate gamma model in temporary data frame
GLODAP_gamma <- GLODAP %>%
  select(depth, lat,
         so_model, thetao_model, lon)

GLODAP_gamma <- GLODAP_gamma %>%
  mutate(CTDPRS = gsw_p_from_z(-depth,
                               lat))

GLODAP_gamma <- GLODAP_gamma %>%
  rename(
    LATITUDE = lat,
    LONGITUDE = lon,
    SALNTY = so_model,
    THETA = thetao_model
  )

source_python(
  paste(
    path_root,
    "/utilities/functions/python_scripts/",
    "Gamma_GLODAP_python.py",
    sep = ""
  )
)

GLODAP_gamma <- calculate_gamma(GLODAP_gamma)

# join gamma column with original data frame
GLODAP <- GLODAP %>%
  mutate(gamma_model = GLODAP_gamma$GAMMA)

GLODAP_NA_filled <- GLODAP

rm(GLODAP_gamma)

# Replace model value with NA, if observations are NA
GLODAP$so_model <-
  ifelse(is.na(GLODAP$sal), NA, GLODAP$so_model)

GLODAP$thetao_model <-
  ifelse(is.na(GLODAP$theta), NA, GLODAP$thetao_model)

GLODAP$temp_model <-
  ifelse(is.na(GLODAP$temp), NA, GLODAP$temp_model)

GLODAP$dissic_model <-
  ifelse(is.na(GLODAP$tco2), NA, GLODAP$dissic_model)

GLODAP$talk_model <-
  ifelse(is.na(GLODAP$talk), NA, GLODAP$talk_model)

GLODAP$o2_model <-
  ifelse(is.na(GLODAP$oxygen), NA, GLODAP$o2_model)

GLODAP$no3_model <-
  ifelse(is.na(GLODAP$nitrate), NA, GLODAP$no3_model)

GLODAP$po4_model <-
  ifelse(is.na(GLODAP$phosphate), NA, GLODAP$po4_model)

GLODAP$si_model <-
  ifelse(is.na(GLODAP$silicate), NA, GLODAP$si_model)

GLODAP$aou_model <-
  ifelse(is.na(GLODAP$aou), NA, GLODAP$aou_model)


# write file for GLODAP observations + subsetted model variables
GLODAP %>%
  group_by(model) %>%
  group_walk(~ write_csv(
    .x,
    paste(
      path_preprocessing,
      .y$model,
      "_GLODAPv2.2021_preprocessed_model_runA_both_ann.csv",
      sep = ""
    )
  ))

GLODAP_NA_filled %>%
  group_by(model) %>%
  group_walk(~ write_csv(
    .x,
    paste(
      path_preprocessing,
      .y$model,
      "_GLODAPv2.2021_preprocessed_model_runA_both_NA_filled_ann.csv",
      sep = ""
    )
  ))

# remove GLODAP observations and rename model subset
GLODAP <- GLODAP %>%
  select(-c(
    sal,
    theta,
    temp,
    tco2,
    talk,
    oxygen,
    nitrate,
    phosphate,
    silicate,
    aou,
    gamma
  )) %>%
  rename(
    sal = so_model,
    theta = thetao_model,
    temp = temp_model,
    tco2 = dissic_model,
    talk = talk_model,
    oxygen = o2_model,
    nitrate = no3_model,
    phosphate = po4_model,
    silicate = si_model,
    aou = aou_model,
    gamma = gamma_model
  )

GLODAP_NA_filled <- GLODAP_NA_filled %>%
  select(-c(
    sal,
    theta,
    temp,
    tco2,
    talk,
    oxygen,
    nitrate,
    phosphate,
    silicate,
    aou,
    gamma
  )) %>%
  rename(
    sal = so_model,
    theta = thetao_model,
    temp = temp_model,
    tco2 = dissic_model,
    talk = talk_model,
    oxygen = o2_model,
    nitrate = no3_model,
    phosphate = po4_model,
    silicate = si_model,
    aou = aou_model,
    gamma = gamma_model
  )

```

# Write files

```{r write_files}

# write final file for GLODAP-based subsetting model variables
GLODAP %>%
  select(-row_number) %>%
  group_by(model) %>%
  group_walk( ~ write_csv(
    .x,
    paste(
      path_preprocessing,
      .y$model,
      "_GLODAPv2.2021_preprocessed_model_runA_final_ann.csv",
      sep = ""
    )
  ))

GLODAP_NA_filled %>%
  select(-row_number) %>%
  group_by(model) %>%
  group_walk(~ write_csv(
    .x,
    paste(
      path_preprocessing,
      .y$model,
      "_GLODAPv2.2021_preprocessed_model_runA_final_NA_filled_ann.csv",
      sep = ""
    )
  ))
  
```


```{r test_for_interpolation, eval=FALSE}

GLODAP <-
  read_csv(paste(path_GLODAP_preprocessing,
                 "GLODAPv2.2021_preprocessed.csv",
                 sep = ""))

GLODAP <- GLODAP %>%
  mutate(month = month(date))

# select GLODAP data for 2019
GLODAP_2019 <- GLODAP %>%
  filter(year == 2018)

# create month x lat x lon grid of observations
Glodap_year_grid_horizontal <- GLODAP_2019 %>%
  select(month, lat, lon) %>%
  unique()

# create month x lat x lon x depth grid of observations
Glodap_year_grid_depth <- GLODAP_2019 %>%
  select(month, lat, lon, depth) %>%
  unique()

# read in cmorized tco2 output in year 2019
variable_data_tibble <-
  read_ncdf(paste(path_cmorized, 
    "dissic_CESM-ETHZ_A_1_gr_1980-2018_v20211122.nc",
    sep = ""
  )) %>%
  as_tibble()

# remove na values
variable_data_tibble <-
  variable_data_tibble %>%
  filter(!is.na(dissic))

# harmonize longitudes
variable_data_tibble <- variable_data_tibble %>%
  mutate(lon = if_else(lon < 20, lon + 360, lon))

# only consider model grids within basinmask
variable_data_tibble <-
  inner_join(variable_data_tibble, basinmask) %>%
  select(-basin_AIP)

# mutate variables
variable_data_tibble <- variable_data_tibble %>%
  mutate(year = year(time_ann) + 1, dissic = as.numeric(dissic)) %>%
  filter(year == 2018) %>%
  select(-time_ann)

# subset model at month x lat x lon grid of observations
model_grid_horizontal <-
  inner_join(Glodap_year_grid_horizontal, variable_data_tibble)

# join model and month x lat x lon x depth grid of observations
model_obs <-
  full_join(model_grid_horizontal, Glodap_year_grid_depth)

# calculate nr of observations per month x lat x lon grid
model_obs <- model_obs %>%
  group_by(month, lat, lon) %>%
  mutate(n = sum(!is.na(dissic))) %>%
  ungroup()

# interpolate variable value from model to observation depth
model_obs_interpo <- model_obs %>%
  filter(n > 1) %>%
  group_by(lon, lat, month) %>%
  arrange(month, lat, lon, depth) %>%
  mutate(dissic_interpolate = approxfun(depth, dissic, rule = 2)(depth)) %>%
  ungroup()

ggplot() +
  geom_path(
    data = model_obs_interpo %>%
      filter(lat == -65.5, lon == 139.5, !is.na(dissic), month == 1) %>%
      arrange(depth),
    aes(dissic, depth, col = "model")
  ) +
  geom_point(
    data = model_obs_interpo %>%
      filter(lat == -65.5, lon == 139.5, !is.na(dissic), month == 1) %>%
      arrange(depth),
    aes(dissic, depth, col = "model")
  ) +
  geom_point(
    data = model_obs_interpo %>%
      filter(lat == -65.5, lon == 139.5, is.na(dissic), month == 1),
    aes(dissic_interpolate, depth, col = "interpolated")
  ) +
  scale_y_reverse() +
  scale_color_brewer(palette = "Dark2", name = "") +
  labs(title = "Interpolation to sampling depth - tco2 of year 2019")

```

```{r test_for_depth_offset, eval=FALSE}

GLODAP_max_depth <- GLODAP %>%
  select(lon, lat, depth) %>%
  group_by(lon, lat) %>%
  summarise(max_depth_GLODAP = max(depth))

model_max_depth <- variable_data_tibble %>%
  select(lon, lat, depth) %>%
  group_by(lon, lat) %>%
  summarise(max_depth_model = max(depth))

GLODAP_model_depth_offset <-
  left_join(GLODAP_max_depth, model_max_depth) %>%
  mutate(offset = max_depth_GLODAP - max_depth_model)

map +
  geom_raster(
    data = GLODAP_model_depth_offset %>% 
      filter(offset > 500),
    aes(lon, lat, fill = offset)
  ) +
  scale_fill_viridis_c(direction =  -1) +
  labs(
    title = "GLODAP-model max sampling depth offset",
    subtitle = "Year 1971 - 2019",
    x = "Longitude",
    y = "Latitude"
  )

```


# GLODAP observations vs cmorized subset comparison

```{r read_GLODAP_with_cmorized_subset_file}


files <- fs::dir_ls(path_preprocessing)

files <- files[str_detect(files, pattern = "preprocessed_model_runA_both_ann.csv")]

GLODAP_cmorized <- files %>% 
  map_dfr(read_csv, .id = "model")

GLODAP_cmorized <- GLODAP_cmorized %>%
  mutate(
    model = str_remove(model, path_preprocessing),
    model = str_remove(
      model,
      "_GLODAPv2.2021_preprocessed_model_runA_both_ann.csv"
    )
  )


```

```{r calc_revelle_factors}


GLODAP_cmorized_beta <- GLODAP_cmorized %>% 
  filter(!is.na(talk),
         !is.na(tco2),
         !is.na(temp),
         !is.na(sal),
         !is.na(pressure),
         !is.na(talk_model),
         !is.na(dissic_model),
         !is.na(temp_model),
         !is.na(so_model)) %>% 
  mutate(
    BetaD = buffer(
      flag = 15,
      var1 = talk* 1e-6,
      var2 = tco2* 1e-6,
      S = sal,
      T = temp,
      k1k2 = "l",
      P = pressure/10,
      Pt = phosphate* 1e-6,
      Sit = silicate* 1e-6,
      warn = "n"
    )$BetaD,
    BetaD_model = buffer(
      flag = 15,
      var1 = talk_model* 1e-6,
      var2 = dissic_model* 1e-6,
      S = so_model,
      T = temp_model,
      k1k2 = "l",
      P = pressure/10,
      Pt = po4_model* 1e-6,
      Sit = si_model* 1e-6,
      warn = "n"
    )$BetaD
  )

```

```{r write_files_with_betaD}

GLODAP_cmorized_beta %>%
  group_by(model) %>%
  group_walk(~ write_csv(
    .x,
    paste(
      path_preprocessing,
      .y$model,
      "_GLODAPv2.2021_preprocessed_model_runA_both_ann_incl_betaD.csv",
      sep = ""
    )
  ))

```


```{r read_files_with_betaD}

files <- fs::dir_ls(path_preprocessing)

files <- files[str_detect(files, pattern = "preprocessed_model_runA_both_ann_incl_betaD.csv")]

GLODAP_cmorized_beta <- files %>% 
  map_dfr(read_csv, .id = "model")

GLODAP_cmorized_beta <- GLODAP_cmorized_beta %>%
  mutate(
    model = str_remove(model, path_preprocessing),
    model = str_remove(
      model,
      "_GLODAPv2.2021_preprocessed_model_runA_both_ann_incl_betaD.csv"
    )
  )


```



```{r GLODAP_vs_cmorized_subset_comparison}


GLODAP_cmorized <- GLODAP_cmorized %>%
  mutate(
    model = str_split(model, "_v", simplify = TRUE)[,1]
  )

GLODAP_cmorized_beta <- GLODAP_cmorized_beta %>%
  mutate(
    model = str_split(model, "_v", simplify = TRUE)[,1]
  )


# for loop across variables
obs_var <-
  c(
    "tco2",
    "talk",
    "oxygen",
    "aou",
    "nitrate",
    "phosphate",
    "silicate",
    "sal",
    "temp",
    "theta",
    "gamma",
    "BetaD"
  )

model_var <-
  c(
    "dissic_model",
    "talk_model",
    "o2_model",
    "aou_model",
    "no3_model",
    "po4_model",
    "si_model",
    "so_model",
    "temp_model",
    "thetao_model",
    "gamma_model",
    "BetaD_model"
  )

for (i in 1:12) {
  #  i <- 1
  
  pdf(
    file = paste0(
      path_preprocessing,
      "models_vs_GLODAP/",
      str_remove(model_var[i], "_model"),
      "_RECCAP2_models_vs_GLODAPv2-2021.pdf"
    ),
    width = 14,
    height = 8
  )
  
  # select correlated observation and model variable
  if (obs_var[i] == "BetaD") {
    GLODAP_cmorized_var <- GLODAP_cmorized_beta %>%
      select(model,
             year,
             month,
             lat,
             lon,
             depth,
             basin_AIP,
             !!sym(obs_var[i]),
             !!sym(model_var[i])) %>%
      drop_na() %>%
      mutate(
        season = case_when(
          month %in% c(3, 4, 5) ~ "Spring",
          month %in% c(6, 7, 8) ~ "Summer",
          month %in% c(9, 10, 11) ~ "Autumn",
          month %in% c(12, 1, 2) ~ "Winter"
        )
      )
  } else{
    GLODAP_cmorized_var <- GLODAP_cmorized %>%
      select(model,
             year,
             month,
             lat,
             lon,
             depth,
             basin_AIP,
             !!sym(obs_var[i]),
             !!sym(model_var[i])) %>%
      drop_na() %>%
      mutate(
        season = case_when(
          month %in% c(3, 4, 5) ~ "Spring",
          month %in% c(6, 7, 8) ~ "Summer",
          month %in% c(9, 10, 11) ~ "Autumn",
          month %in% c(12, 1, 2) ~ "Winter"
        )
      )
  }
  
  # calculate equal axis limits and binwidth
  axis_lims <- GLODAP_cmorized_var %>%
    summarise(max_value = max(c(max(!!sym(
      obs_var[i]
    )),
    max(
      !!sym(model_var[i])
    ))),
    min_value = min(c(min(!!sym(
      obs_var[i]
    )),
    min(
      !!sym(model_var[i])
    ))))
  
  binwidth_value <- (axis_lims$max_value - axis_lims$min_value) / 40
  axis_lims <- c(axis_lims$min_value, axis_lims$max_value)
  
  # obs-model plot (season)
  print(
    ggplot(GLODAP_cmorized_var, aes(
      x = !!sym(obs_var[i]),
      y = !!sym(model_var[i])
    )) +
      geom_bin2d(binwidth = binwidth_value) +
      labs(title = "Observation (x) vs Model (y)",
           subtitle = "Seasonal comparison") +
      scale_fill_viridis_c(trans = "log10") +
      geom_abline(slope = 1,
                  col = 'red') +
      coord_equal(xlim = axis_lims,
                  ylim = axis_lims) +
      facet_grid(season ~ model)
  )
  
  # obs-model plot (year)
  print(
    ggplot(GLODAP_cmorized_var, aes(
      x = !!sym(obs_var[i]),
      y = !!sym(model_var[i])
    )) +
      geom_bin2d(binwidth = binwidth_value) +
      labs(title = "Observation (x) vs Model (y)",
           subtitle = "All years") +
      scale_fill_viridis_c(trans = "log10") +
      geom_abline(slope = 1, col = 'red') +
      coord_equal(xlim = axis_lims,
                  ylim = axis_lims) +
      facet_wrap( ~ model, ncol = 5)
  )
  
  
  # Calculate variable offset
  GLODAP_cmorized_var <- GLODAP_cmorized_var %>%
    mutate(offset = !!sym(model_var[i])-!!sym(obs_var[i]))
  
  # Calculate annual mean offset
  GLODAP_cmorized_var_year <- GLODAP_cmorized_var %>%
    group_by(year, model) %>%
    summarise(offset = mean(offset)) %>%
    ungroup()
  
  muted <- c(colour("muted", names = FALSE)(9),"#999999")

  # plot annual mean offset
  print(
    GLODAP_cmorized_var_year %>%
      ggplot(aes(year, offset, col = model)) +
      geom_point() +
      geom_line() +
      scale_color_manual(values = muted) +
      labs(title = "Annual mean offset",
           subtitle = paste(sym(model_var[i]), "-", sym(obs_var[i]))) +
      theme(legend.position = "bottom",
            legend.title = element_blank())
  )
  
  # spatial distribution of the model-observations offset for 4 depth intervals
  intervals <- c(0, 150, 500, 2000, 8000)
  
  for (j in 1:4) {
    # j <- 1
    GLODAP_cmorized_var_interval <- GLODAP_cmorized_var %>%
      filter(depth >= intervals[j],
             depth < intervals[j + 1])
    
    
    # Calculate annual mean offset
    GLODAP_cmorized_var_year <- GLODAP_cmorized_var_interval %>%
      group_by(year, model) %>%
      summarise(offset = mean(offset)) %>%
      ungroup()
    
    # plot annual mean offset
    print(
      GLODAP_cmorized_var_year %>%
        ggplot(aes(year, offset, col = model)) +
        geom_point() +
        geom_line() +
        labs(
          title = paste(
            "Annual mean offset | Depth interval:",
            intervals[j],
            "-",
            intervals[j + 1],
            "m"
          ),
          subtitle = paste(sym(model_var[i]), "-", sym(obs_var[i]))
        ) +
        
        scale_color_manual(values = muted) +
        theme(legend.position = "bottom",
              legend.title = element_blank())
    )
    
    
    GLODAP_cmorized_var_grid <- GLODAP_cmorized_var_interval %>%
      group_by(lat, lon, model) %>%
      summarise(offset = mean(offset)) %>%
      ungroup()

    # plot mean spatial distribution (model - obs)
    limit <-
      quantile(abs(GLODAP_cmorized_var_grid$offset), 0.98) * c(-1, 1)
    print(
      map +
        geom_raster(data = GLODAP_cmorized_var_grid, aes(lon, lat, fill = offset)) +
        scale_fill_continuous_divergingx(
          palette = "Spectral",
          name = "offset",
          rev = TRUE,
          limit = limit,
          na.value = "black"
        ) +
        labs(
          title = paste(model_var[i],
                        "-",
                        obs_var[i],
                        " | mean offset per grid cell"),
          subtitle = paste(
            "Depth interval:",
            intervals[j],
            "-",
            intervals[j + 1],
            "m | black: outside 98th percentile"
          ),
          x = "Longitude",
          y = "Latitude"
        ) +
        facet_wrap( ~ model, ncol = 4)
    )
    
    print(
      GLODAP_cmorized_var_grid %>%
        ggplot(aes(offset)) +
        geom_vline(xintercept = limit) +
        geom_histogram() +
        labs(
          title = paste(
            model_var[i],
            " - ",
            obs_var[i],
            "mean offset per grid cell | histogram + abs. 98th Percentile"
          ),
          subtitle = paste("Depth interval:",
                           intervals[j], "-", intervals[j + 1], "m")
        ) +
        coord_cartesian(expand = FALSE) +
        facet_wrap(~ model, ncol = 3)
    )
  }
  
  # zonal mean section of the model-observations offset for each basin
  for (i_basin_AIP in unique(GLODAP_cmorized_var$basin_AIP)) {
    # i_basin_AIP = "Atlantic"
    GLODAP_cmorized_var_zonal <- GLODAP_cmorized_var %>%
      filter(basin_AIP == i_basin_AIP) %>%
      group_by(lat, depth, model) %>%
      summarise(offset = mean(offset, na.rm = TRUE)) %>%
      ungroup()
    
    # plot zonal mean section (model - obs)
    lat_max <- params_global$lat_max
    lat_min <- params_global$lat_min
    limit <-
      quantile(abs(GLODAP_cmorized_var_zonal$offset), 0.98) * c(-1, 1)
    
    print(
      GLODAP_cmorized_var_zonal %>%
        ggplot(aes(lat, depth, z = offset)) +
        stat_summary_2d(binwidth = c(1, 100)) +
        scale_fill_continuous_divergingx(
          palette = "Spectral",
          name = "offset",
          rev = TRUE,
          limit = limit,
          na.value = "black"
        ) +
        coord_fixed(expand = 0,
                        xlim = c(lat_min, lat_max),
                    ratio = 0.01) +
        scale_y_reverse(limits = c(6000, 0),
                        breaks = seq(0,6000,2000)) +
        labs(
          title = paste(model_var[i],
                        "-",
                        obs_var[i],
                        " | zonal mean offset"),
          subtitle = paste("Basin:",
                           i_basin_AIP,
            " | black: outside 98th percentile"),
          x = "Latitude (°N)",
          y = "Depth (m)"
        ) +
        facet_wrap(~ model, ncol = 4)
    )
  }
  
  dev.off()
}

```
