---
title: "Random subset"
author: "Jens Daniel Müller"
date:  "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  workflowr::wflow_html:
    number_sections: true
    toc_depth: 3
    toc_float:
      collapsed: false
editor_options:
  chunk_output_type: console
---

```{r parent, child = "/nfs/kryo/work/jenmueller/emlr_cant/utilities/setup.Rmd"}
# this chunk runs the code stored in setup.Rmd
# if required, please refer to instructions given here:
# https://jdblischak.github.io/workflowr/articles/wflow-07-common-code.html
```

```{r define_paths}
path_GLODAP_preprocessing <-
  paste(path_root, "/observations/preprocessing/", sep = "")
path_cmorized <-
  "/nfs/kryo/work/loher/CESM_output/RECCAP2/cmorized_Dec2020/split_monthly/"
path_preprocessing  <-
  paste(path_root, "/model/preprocessing/", sep = "")
```

```{r load_libraries_specific, include=FALSE}
library(stars)
library(lubridate)
library(rqdatatable)
library(gsw)
library(marelac)
```

```{r select_basin_mask}

# use only three basin to assign general basin mask
# ie this is not specific to the MLR fitting
basinmask <- basinmask %>%
  filter(MLR_basins == "2") %>%
  select(lat, lon, basin_AIP)

```

# Read GLODAPv2_2020 preprocessed files

```{r read_GLODAPv2_2020_preprocessed_file}

GLODAP <-
  read_csv(paste(path_GLODAP_preprocessing,
                 "GLODAPv2.2020_preprocessed.csv",
                 sep = ""))

GLODAP <- GLODAP %>%
  mutate(month = month(date))

```

# Randomly subset model data

Here we randomly subset cmorized (1x1) model with variable forcing, according to the total number of GLODAP observations for the whole period from a previously cleaned file. The number for the annual subset remains the same for each year, which could be expressed by the total number of observations divided by number of years.

Besides, Model results are given in [mol m^-3^], whereas GLODAP data are in [µmol kg^-1^]. This refers to the variables:

- DIC  
- ALK  
- O2  
- NO3  
- PO4  
- SiO3  
- AOU (calculated)

For comparison, model results were converted from [mol m^-3^] to [µmol kg^-1^]

```{r random_subset_cmorized_variable_forcing_data}
# read in a random model
model <-
  read_ncdf(paste(path_cmorized, "dissic_CESM-ETHZ_A_1_gr_1982.nc", sep = "")) %>%
  as_tibble() %>%
  drop_na()

# convert longitudes and mutate month
model <- model %>%
  mutate(lon = if_else(lon < 20, lon + 360, lon)) %>%
  mutate(month = month(time_mon))

# only consider model grids within basinmask
model <- inner_join(model, basinmask)

# model grid with depth
model_grid_depth <- model %>%
  select(month, lat, lon, depth)

rm(model)

# set name of model to be subsetted
model_ID <- "A"

# for loop across years
years <- c("1982":"2019")

# set equal number of random model sampling will be made for each year
n = floor(nrow(GLODAP) / length(years))

for (i_year in years) {
  # i_year <- years[1]
  
  # random sample n = GLODAP / years from model grid depth
  model_resample_grid_depth <- sample_n(model_grid_depth, n) %>%
    arrange(lat, lon, depth, month) %>%
    mutate(year = i_year)
  
  # for loop across variables
  variables <-
    c("so", "thetao", "dissic", "talk", "o2", "no3", "po4", "si")
  
  for (i_variable in variables) {
    # i_variable <- variables[2]
    
    # read list of all files
    file <-
      list.files(
        path = path_cmorized,
        pattern = paste(
          "^",
          i_variable,
          "_CESM-ETHZ_",
          model_ID,
          "_1_gr_",
          i_year,
          ".nc",
          sep = ""
        )
      )
    print(file)
    
    # read in data
    variable_data <-
      read_ncdf(paste(path_cmorized,
                      file,
                      sep = ""))
    
    # convert to tibble
    variable_data_tibble <- variable_data %>%
      as_tibble()
    
    # remove open link to nc file
    rm(variable_data)
    
    # remove na values
    variable_data_tibble <-
      variable_data_tibble %>%
      filter(!is.na(!!sym(i_variable)))
    
    # convert longitudes
    variable_data_tibble <- variable_data_tibble %>%
      mutate(lon = if_else(lon < 20, lon + 360, lon))
    
    # only consider model grids within basinmask
    variable_data_tibble <- inner_join(variable_data_tibble, basinmask) %>%
      select(-basin_AIP)
    
    # mutate variables
    variable_data_tibble <- variable_data_tibble %>%
      mutate(month = month(time_mon),
             !!sym(i_variable) := as.numeric(!!sym(i_variable))) %>%
      select(-time_mon)
    
    # random sample for each model variable in specific year
    model_resample_grid_depth <-
      left_join(model_resample_grid_depth, variable_data_tibble)
  }
  
  # add random sample model subset for each year together
  if (exists("model_resample")) {
    model_resample <-
      bind_rows(model_resample, model_resample_grid_depth)
  }
  
  if (!exists("model_resample")) {
    model_resample <- model_resample_grid_depth
  }
  
}

# calculate model temperature
model_resample <- model_resample %>%
  mutate(temp = gsw_pt_from_t(
    SA = so,
    t = thetao,
    p = 10.1325,
    p_ref = depth
  ))

# unit transfer from mol/m3 to µmol/kg
model_resample <- model_resample %>%
  mutate(
    rho = gsw_pot_rho_t_exact(
      SA = so,
      t = temp,
      p = depth,
      p_ref = 10.1325
    ),
    dissic = dissic * (1e+6 / rho),
    talk = talk * (1e+6 / rho),
    o2 = o2 * (1e+6 / rho),
    no3 = no3 * (1e+6 / rho),
    po4 = po4 * (1e+6 / rho),
    si = si * (1e+6 / rho)
  )

# calculate AOU
model_resample <- model_resample %>%
  mutate(
    oxygen_sat_m3 = gas_satconc(
      S = so,
      t = temp,
      P = 1.013253,
      species = "O2"
    ),
    oxygen_sat_kg = oxygen_sat_m3 * (1e+3 / rho),
    aou = oxygen_sat_kg - o2
  ) %>%
  select(-oxygen_sat_kg,-oxygen_sat_m3)

# write file for random model sampling
model_resample %>%
  write_csv(paste(path_preprocessing,
                  "GLODAPv2.2020_preprocessed_model_runA_random_subset.csv",
                  sep = ""))

```

# Control plots

## Spatial distribution

```{r random_sample_distribution_maps}

# read in random model sampling file
model_resample <-
  read_csv(paste(path_preprocessing,
                 "GLODAPv2.2020_preprocessed_model_runA_random_subset.csv",
                 sep = ""))

# plot random sampling cmorized grids in each year
years <- c("1982", "1990", "2000", "2010", "2019")
for (i_year in years) {
  # i_year <- years[1]
  
  model_resample_year <- model_resample %>%
    filter(year == i_year)
  
  print(
    map +
      geom_bin2d(data = model_resample_year,
                 aes(lon, lat),
                 binwidth = 1) +
      scale_fill_viridis_c(direction = -1) +
      coord_quickmap(expand = 0) +
      labs(
        title = paste("Random Model Sampling of year", i_year),
        subtitle = paste("Nr of observations", nrow(model_resample_year)),
        x = "Longitude",
        y = "Latitude"
      )
  )

}

```

## Depth distribution

```{r random_sample_depth_distribution}

# Calculate and plot depth distribution of model subset
model_resample_depth <- model_resample %>%
  count(depth, year)

model_resample_depth_average <- model_resample_depth %>%
  group_by(depth) %>%
  summarise(n = mean(n))

model_resample_depth_average %>%
  arrange(depth) %>%
  ggplot(aes(n, depth)) +
  geom_point(data = model_resample_depth,
             aes(n, depth, col = "All years")) +
  geom_point(aes(n, depth, col = "Average")) +
  geom_path(aes(n, depth, col = "Average")) +
  scale_color_brewer(palette = "Set1",
                     name = "",
                     direction = -1) +
  scale_y_reverse() +
  coord_cartesian(xlim = c(0,500),
                  ylim = c(6000,0)) +
  labs(title = "Depth distribution of random model subset")


```

```{r GLODAP_depth_distribution}

# Calculate and plot depth distribution of GLODAP data
# Depths gridded to model depth levels for comparison
GLODAP_depth <- GLODAP %>%
  mutate(depth = as.numeric(as.character(cut(depth,
                     c(0,unique(model_resample_depth_average$depth)),
                     labels = unique(model_resample_depth_average$depth))))) %>% 
  count(depth, year)

GLODAP_depth_average <- GLODAP_depth %>%
  group_by(depth) %>%
  summarise(n = mean(n))

GLODAP_depth_average %>%
  arrange(depth) %>%
  ggplot(aes(n, depth)) +
  geom_point(data = GLODAP_depth,
             aes(n, depth, col = "All years")) +
  geom_point(aes(n, depth, col = "Average")) +
  geom_path(aes(n, depth, col = "Average")) +
  scale_color_brewer(palette = "Set1",
                     name = "",
                     direction = -1) +
  scale_y_reverse() +
  coord_cartesian(xlim = c(0,500),
                  ylim = c(6000,0)) +
  labs(title = "Depth distribution of GLODAP observations")

```
